---
title: "``Minstress``: Better Starting Configuration For Non-Metric MDS"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(analytics)
```



#### Description
Minstress is a heuristic to find better non-metric MDS solutions, by finding better starting configurations, instead of just using a random one.

#### Usage
<pre><code>
Minstress(x, p, s, k, iter = 5, pb = F, m = "euclidean")
</code></pre>

#### Arguments

* x a data frame containing numeric values only
* p the size of the population of seeds (any positive integer)
* s the number of seeds we sample (any positive integer)
* k the number of dimensions wanted (any positive integer)
* iter a positive integer specifying the number of iterations.
* pb a Boolean variable declaring if one wants to display a pogress bar (default:False)
* m a string specifying the distance method (default: ’euclidean’)

#### Details
This function performs several iterations, each using a different starting seed, and in turn each one of
those iterations performs non-metric MDS many times (typically, thousands or more) in an attempt
to find the best seed (which induces a particular initial configuration) of them all.

#### Value
A list informing about dimensionality, minimum STRESS level found, and best seed found. One
can then use the best seed found to perform non-metric MDS with a better initial configuration
(generally).

#### Author(s)
Albert Dorador

#### Examples
```{r}
require(MASS)
swiss.x <- as.data.frame(swiss[, -1])
Minstress(swiss.x, 1e5, 50, 2, iter = 3)
```

```{r}
# Comparing without using Minstress (for such a low value of s, difference is minimal)
swiss.x <- as.matrix(swiss[, -1])
swiss.dist <- dist(swiss.x)
swiss.mds <- isoMDS(swiss.dist)
```
