---
title: "``offliers``:  Takes Outliers Off"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(analytics)
```


#### Description

offliers Finds the existing outliers after fitting a linear model, according to various criteria.

#### Usage

<pre><code>
offliers(dataset, mod, CD = TRUE, DFB = FALSE, COVR = FALSE,
pctg = 100, intersection = TRUE)
</code></pre>

#### Arguments
* ``dataset``: an object containing the data used in the linear regression model, typically a data frame.
* ``mod``: an object of class "lm" (the model fitted by the user).
* ``CD``: a Boolean variable, indicating whether the Cook’s Distance criterion is to be used.
* ``DFB``: a Boolean variable, indicating whether the DFBetas criterion is to be used.
* ``COVR``: a Boolean variable, indicating whether the COVRATIO criterion is to be used.
* ``pctg``: a real number between 0 and 100, indicating the maximum percentage of original observations to be removed.
* ``intersection``: a Boolean variable, indicating whether the intersection or the union of the outliers detected must be considered (in case more than one criterion has been selected).


#### Value
a list containing, according to each criterion selected, which observations have been identified as
outliers, how many they are, what percentage of the total number of observations they represent,
and, if more than one criterion has been selected, the final outliers, quantity and percentage.

#### Examples
```{r}
require(graphics)
## Annette Dobson (1990) "An Introduction to Generalized Linear Models".
## Page 9: Plant Weight Data.
ctl <- c(4.17,5.58,5.18,6.11,4.50,4.61,5.17,4.53,5.33,5.14)
trt <- c(4.81,4.17,4.41,3.59,5.87,3.83,6.03,4.89,4.32,4.69)
group <- gl(2, 10, 20, labels = c("Ctl","Trt"))
weight <- c(ctl, trt)
lm.D9 <- lm(weight ~ group)
db <- data.frame(weight, group)

offliers(db,lm.D9)
offliers(db,lm.D9, CD = FALSE, DFB = TRUE, COVR = TRUE)
offliers(db,lm.D9, CD = TRUE, DFB = TRUE, COVR = TRUE, intersection = FALSE)
offliers(db,lm.D9, CD = TRUE, DFB = TRUE, COVR = TRUE, pctg = 10, intersection = FALSE)
```

#### Details
Criteria available: Cook’s Distance, DFBetas, and COVRATIO. DFFits has not been included because it is conceptually equivalent to Cook’s Distance; in fact there’s a closed-form formula to
convert one value to the other. See references. The user can select any combination of those, and take off the outliers in the intersection (default) or union.


#### Author(s)
Albert Dorador

#### References
`* Cook & Weisberg 1982, "Residuals and Influence in Regression". http://conservancy.umn.edu/handle/11299/37076

