---
title: "``Wbiplot``:  Weighted Biplot"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(analytics)
```



#### Description
Wbiplot produces a biplot with any weight distribution between Row and Column markers. 
This way the full spectrum from perfect row resolution (Row-metric preserving biplot) to perfect column resolution (Column-metric preserving biplot) is available.

#### Usage
<pre><code>
Wbiplot(df, numer1, denom1 = 1, numer2, denom2 = 1, cx = 0.5)
</code><pre>

#### Arguments
* ``df``: a dataframe with numeric values only
* ``numer1``: numerator of first exponent (can be a decimal*)
* ``denom1``: denominator of first exponent (*default: 1*)
* ``numer2``: numerator of second exponent (*can be a decimal*)
* ``denom2``: denominator of second exponent (*default: 1*)
* ``cx``: graphical magnification factor (*default: 0.5*)

#### Examples
```{r}
require(graphics)
# Exemple 1: Row metric preserving
Wbiplot(USArrests, numer1 = 1, numer2 = 0, cx = 0.6)
```
```{r}
# Exemple 2: Column metric preserving
Wbiplot(USArrests, numer1 = 0, numer2 = 1, cx = 0.6)
# Comparison with function biplot from package stats
biplot(princomp(USArrests), cex = 0.6)
```
```{r}
# Example 3: Custom, 50-50
Wbiplot(USArrests, numer1 = 0.5, numer2 = 0.5)
```
```{r}
# Example 4: Custom, 20-80
Wbiplot(USArrests, numer1 = 0.2, numer2 = 0.8)
weakly.stationary 13
```


#### Details
This function makes use of function Matpow from package powerplus to be able to raise any valid matrix (see ``Matpow`` documentation) to any real power between 0 and 1 included.

#### Value
A biplot of a dataframe with the specified weights. Weights can either be supplied as two fractions, or as two decimal numbers.

#### Author(s)
Albert Dorador

#### See Also
Matpow
