---
title: "``auc_compare``: Compare AUC values using the FBH method."
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(auctestr)
```


#### Description
Apply the FBH method to compare outcome_col by compare_col, averaging over ``time_col`` (due to non-independence) and then over over_col by using Stouffer’s Method.

#### Usage

<pre><code>
auc_compare(df, compare_values, filter_value, time_col = "time",
outcome_col = "auc", compare_col = "model_id", over_col = "dataset",
n_col = "n", n_p_col = "n_p", n_n_col = "n_n",
filter_col = "model_variant")
</code></pre>

#### Arguments
* ``df``: DataFrame containing time_col, outcome_col, compare_col, and over_col.
* ``compare_values``: names of models to compare (character vector of length 2). These should match exactly the names as they appear in ``compare_col``.
* ``filter_value``: (optional) keep only observations which contain filter_value for ``filter_col``.
* ``time_col``: name of column in df representing time of observations (z-scores are averaged over time_col within each model/dataset due to non-independence). These can also be other dependent groupings, such as cross-validation folds.
* ``outcome_col``: name of column in df representing outcome to compare; this should be Area Under the Receiver Operating Characteristic or statistic (this method applies specifically to AUC and not other metrics (i.e., sensitivity, precision, F1)..
* ``compare_col``: name of column in df representing two conditions to compare (should contain at least 2 unique values; these two values are specified as compare_values).
* over_col identifier for independent experiments, iterations, etc. over which z-scores for models are to be compared (using Stouffer's Z).
* ``n_col``: name of column in df with total number of observations in the sample tested by each row.
* ``n_p_col``: name of column in df with n_p, number of positive observations.
* ``n_n_col``: name of column in df with n_n, number of negative observations.
* ``filter_col``: (optional) name of column in df to filter observations on; keep only observations which contain filter_value for ``filter_col``.

#### Examples
```{r}
## load sample experiment data
data(sample_experiment_data)
## compare VariantA of ModelA and ModelB
auc_compare(sample_experiment_data,
compare_values = c('ModelA', 'ModelB'),
filter_value = c('VariantA'),
time_col = 'time',
outcome_col = 'auc',
compare_col = 'model_id',
over_col = 'dataset',
filter_col = 'model_variant')
```

```{r}
## compare VariantC of ModelA and ModelB
auc_compare(sample_experiment_data,
compare_values = c('ModelA', 'ModelB'),
filter_value = c('VariantC'),
time_col = 'time',
outcome_col = 'auc',
compare_col = 'model_id',
over_col = 'dataset',
filter_col = 'model_variant')
```

```{r}
## compare ModelC, VariantA and VariantB
auc_compare(sample_experiment_data,
compare_values = c('VariantA', 'VariantB'),
filter_value = c('ModelC'),
time_col = 'time',
outcome_col = 'auc',
compare_col = 'model_variant',
over_col = 'dataset',
filter_col = 'model_id')
```


#### Value
numeric, overall z-score of comparison using the FBH method.

#### References
* Fogarty, Baker and Hudson, Case Studies in the use of ROC Curve Analysis for Sensor-Based Estimates in Human Computer Interaction, Proceedings of Graphics Interface (2005) pp. 129-136.
* Stouffer, S.A.; Suchman, E.A.; DeVinney, L.C.; Star, S.A.; Williams, R.M. Jr. The American Soldier, Vol.1: Adjustment during Army Life (1949).

#### See Also
Other fbh method: fbh_test, se_auc
