---
title: "``auctestr::se_auc``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(auctestr)
```

## ``auctestr::se_auc`` 

Compute standard error of AUC score, using its equivalence to the Wilcoxon statistic.

#### Description
Compute standard error of AUC score, using its equivalence to the Wilcoxon statistic.

#### Usage
<pre><code>
se_auc(auc, n_p, n_n)
</code></pre>

#### Arguments

* ``auc``: value of Area statistic (or AUC, or Area Under the Receiver operating characteristic curve) (numeric).
* ``n_p``: number of positive cases (integer).
* ``n_n``: number of negative cases (integer).


####Examples

```{r}
se_auc(0.75, 20, 200)
## standard error decreases when data become more balanced over
## positive/negative outcome class, holding sample size fixed
se_auc(0.75, 110, 110)
## standard error increases when sample size shrinks
se_auc(0.75, 20, 20)
```

#### References
* Hanley and McNeil, The meaning and use of the area under a receiver operating characteristic (ROC) curve. Radiology (1982) 43 (1) pp. 29-36.
* Fogarty, Baker and Hudson, Case Studies in the use of ROC Curve Analysis for Sensor-Based Estimates in Human Computer Interaction, Proceedings of Graphics Interface (2005) pp. 129-136.

