---
title: "``centerTime``:  Move the window such that the given time is centered"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(timeVis)
```



### ### Description
Move the window such that the given time is centered
### Usage
centerTime(id, time, options)
#### Arguments 
* id Timeline id or a timevis object (the output from timevis())
* time The date/time to center around
* options Named list of options controlling the animation. Most common option is "animation" = TRUE/FALSE.
For a full list of options, see the "moveTo" method in the official Timeline documentation

#### Examples
```{r}
timevis() %>%
  centerTime(Sys.Date() - 1)


if (interactive()) {
  library(shiny)
  shinyApp(
    ui = fluidPage(
      timevisOutput("timeline"),
      actionButton("btn", "Center around 24 hours ago")
    ),
    server = function(input, output) {
      output$timeline <- renderTimevis(
        timevis()
      )
      observeEvent(input$btn, {
        centerTime("timeline", Sys.Date() - 1)
      })
    }
  )
}
```