---
title: "``timevis::setSelection``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(timeVis)
```

#### Description
Select one or multiple items on a timeline

### Usage
<pre><code>
setSelection(id, itemId, options)
</code></pre>

#### Arguments 
* ``id``: Timeline id or a timevis object (the output from timevis())
* ``itemId``: A vector (or single value) of the item ids to select
* ``options``: Named list of options controlling mainly the animation. Most common options are focus = TRUE/FALSE and "animation" = TRUE/FALSE. For a full list of options, see the "setSelection" method in the official Timeline documentation

#### Examples
```{r}
timevis(data.frame(id = 1:3, start = Sys.Date(), content = 1:3)) %>%
  setSelection(2)
if (interactive()) {
  library(shiny)
  shinyApp(
    ui = fluidPage(
      timevisOutput("timeline"),
      actionButton("btn", "Select item 2")
    ),
    server = function(input, output) {
      output$timeline <- renderTimevis(
        timevis(
          data.frame(id = 1:3, start = Sys.Date(), content = 1:3)
        )
      )
      observeEvent(input$btn, {
        setSelection("timeline", 2)
      })
    }
  )
}
```