---
title: "``accessors``:  Access or set information on cross-validation results"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(cvTools)
```



#### Description 

Retrieve or set the names of cross-validation results, retrieve or set the identifiers of the models, orretrieve the number of cross-validation results or included models.

#### Usage 
<pre><code>
cvNames(x)
cvNames(x) <- value
fits(x)
fits(x) <- value
ncv(x)
nfits(x)
</code></pre>
#### Arguments 

* x an object inheriting from class "cv" or "cvSelect" that contains cross-validation results.
* value a vector of replacement values.

#### Value
* cvNames returns the names of the cross-validation results. The replacement function thereby returns
them invisibly.
* fits returns the identifiers of the models for objects inheriting from class "cvSelect" and NULL for
objects inheriting from class "cv". The replacement function thereby returns those values invisibly.
* ncv returns the number of cross-validation results.
* nfits returns the number of models included in objects inheriting from class "cvSelect" and NULL for objects inheriting from class "cv".

#### Author(s)
Andreas Alfons

#### See Also
cvFit, cvSelect, cvTuning

#### Examples 
```{r}

library("robustbase")
data("coleman")
set.seed(1234) # set seed for reproducibility
## set up folds for cross-validation
folds <- cvFolds(nrow(coleman), K = 5, R = 10)
## compare raw and reweighted LTS estimators for
## 50% and 75% subsets
```
```{r}
# 50% subsets
fitLts50 <- ltsReg(Y ~ ., data = coleman, alpha = 0.5)
cvFitLts50 <- cvLts(fitLts50, cost = rtmspe, folds = folds,
fit = "both", trim = 0.1)
```
```{r}
# 75% subsets
fitLts75 <- ltsReg(Y ~ ., data = coleman, alpha = 0.75)
cvFitLts75 <- cvLts(fitLts75, cost = rtmspe, folds = folds,
fit = "both", trim = 0.1)
# combine results into one object
cvFitsLts <- cvSelect("0.5" = cvFitLts50, "0.75" = cvFitLts75)
cvFitsLts
```
```{r}
# "cv" object
ncv(cvFitLts50)
nfits(cvFitLts50)
cvNames(cvFitLts50)
cvNames(cvFitLts50) <- c("improved", "initial")
fits(cvFitLts50)
aggregate.cv 5
```
```{r}
# "cvSelect" object
ncv(cvFitsLts)
nfits(cvFitsLts)
cvNames(cvFitsLts)
cvNames(cvFitsLts) <- c("improved", "initial")
fits(cvFitsLts)
fits(cvFitsLts) <- 1:2
cvFitsLts
