---
title: "``cvFolds `` Cross-validation folds"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(cvTools)
```



#### Description 

Split n observations into K groups to be used for (repeated) K-fold cross-validation. K should
thereby be chosen such that all groups are of approximately equal size.

#### Usage 

<pre><code>
cvFolds(n, K = 5, R = 1, type = c("random", "consecutive", "interleaved"))
</code></pre>

#### Arguments 

* ``n``: an integer giving the number of observations to be split into groups.
* ``K``: an integer giving the number of groups into which the observations should be split (the default is five). Setting K equal to n yields leave-one-out crossvalidation.
* ``R``: an integer giving the number of replications for repeatedK-fold cross-validation.
This is ignored for for leave-one-out cross-validation and other non-random splits of the data.
* ``type``: a character string specifying the type of folds to be generated. Possible values are "random" (the default), "consecutive" or "interleaved".

#### Value
An object of class "cvFolds" with the following components:
* n an integer giving the number of observations.
* K an integer giving the number of folds.
* R an integer giving the number of replications.
* subsets an integer matrix in which each column contains a permutation of the indices.
which an integer vector giving the fold for each permuted observation.


#### Examples 
```{r}

set.seed(1234) # set seed for reproducibility
cvFolds(20, K = 5, type = "random")
cvFolds(20, K = 5, type = "consecutive")
cvFolds(20, K = 5, type = "interleaved")
cvFolds(20, K = 5, R = 10)
```

#### Author(s)
Andreas Alfons
See Also
cvFit, cvSelect, cvTuning
