---
title: "``dotplot.cv   ``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(cvTools)
```

Dot plots of cross-validation results

#### Description 

Produce dot plots of (average) results from (repeated) K-fold cross-validation.

#### Usage 
<pre><code>

## S3 method for class 'cv'
dotplot(x, data, select = NULL,
seFactor = NA, ...)
## S3 method for class 'cvSelect'
dotplot(x, data, subset = NULL,
select = NULL, seFactor = x$seFactor, ...)

</code></pre>
#### Arguments 

* x an object inheriting from class "cvSelect" that contains cross-validation results. data currently ignored.
subset a character, integer or logical vector indicating the subset of models for which
to plot the cross-validation results.
select a character, integer or logical vector indicating the columns of cross-validation
results to be plotted.
* seFactor a numeric value giving the multiplication factor of the standard error for displaying
error bars. Error bars can be suppressed by setting this to NA.
... additional  Arguments to be passed to the "formula" method of dotplot.


#### Examples 
```{r}

library("robustbase")
data("coleman")
set.seed(1234) # set seed for reproducibility
## set up folds for cross-validation
folds <- cvFolds(nrow(coleman), K = 5, R = 10)
## compare LS, MM and LTS regression
# perform cross-validation for an LS regression model
fitLm <- lm(Y ~ ., data = coleman)
cvFitLm <- cvLm(fitLm, cost = rtmspe,
folds = folds, trim = 0.1)
```

```{r}
# perform cross-validation for an MM regression model
fitLmrob <- lmrob(Y ~ ., data = coleman, k.max = 500)
cvFitLmrob <- cvLmrob(fitLmrob, cost = rtmspe,
folds = folds, trim = 0.1)
```

```{r}
# perform cross-validation for an LTS regression model
fitLts <- ltsReg(Y ~ ., data = coleman)
cvFitLts <- cvLts(fitLts, cost = rtmspe,
folds = folds, trim = 0.1)
# combine and plot results
cvFits <- cvSelect(LS = cvFitLm, MM = cvFitLmrob, LTS = cvFitLts)
cvFits
dotplot(cvFits)
```

```{r}
## compare raw and reweighted LTS estimators for
## 50% and 75% subsets
# 50% subsets
fitLts50 <- ltsReg(Y ~ ., data = coleman, alpha = 0.5)
cvFitLts50 <- cvLts(fitLts50, cost = rtmspe, folds = folds,
fit = "both", trim = 0.1)
# 75% subsets
fitLts75 <- ltsReg(Y ~ ., data = coleman, alpha = 0.75)
cvFitLts75 <- cvLts(fitLts75, cost = rtmspe, folds = folds,
fit = "both", trim = 0.1)
```

```{r}
# combine and plot results
cvFitsLts <- cvSelect("0.5" = cvFitLts50, "0.75" = cvFitLts75)
cvFitsLts
dotplot(cvFitsLts)
```

#### Details 

For objects with multiple columns of repeated cross-validation results, conditional dot plots are
produced.
Value
An object of class "trellis" is returned invisibly. The update method can be used to update components
of the object and the print method (usually called by default) will plot it on an appropriate
plotting device.
dotplot.cv 29
Author(s)
Andreas Alfons
See Also
cvFit, cvSelect, cvTuning, plot, xyplot, bwplot, densityplot
