
plot.cv Plot cross-validation results

#### Description 

Plot results from (repeated) K-fold cross-validation.

#### Usage 
<pre><code>

## S3 method for class 'cv'
plot(x,
  method = c("bwplot", "densityplot", "xyplot", "dotplot"),
  ...)
## S3 method for class 'cvSelect'
plot(x,
  method = c("bwplot", "densityplot", "xyplot", "dotplot"),
  ...)

</code></pre>

#### Arguments 

* ``x``: an object inheriting from class "cv" or "cvSelect" that contains cross-validation results.
* ``method``@ a character string specifying the type of plot. For the "cv" method, possible values are "bwplot" to create a box-and-whisker plot via bwplot (the default), or "densityplot" to create a kernel density plot via densityplot. Note that
those plots are only meaningful for results from repeated cross-validation. For the "cvSelect" method, there are two additional possibilities: "xyplot" to plot the (average) results for each model via xyplot, or "dotplot" to create a similar
dot plot via dotplot. The default is to use "bwplot" for results from repeated cross-validation and "xyplot" otherwise. In any case, partial string matching allows supply abbreviations of the accepted values.
* ... additional Arguments  to be passed down.


#### Examples 
```{r}

library("robustbase")
data("coleman")
set.seed(1234) # set seed for reproducibility
# set up folds for cross-validation
folds <- cvFolds(nrow(coleman), K = 5, R = 50)
## compare LS, MM and LTS regression
# perform cross-validation for an LS regression model
fitLm <- lm(Y ~ ., data = coleman)
cvFitLm <- cvLm(fitLm, cost = rtmspe,
folds = folds, trim = 0.1)
```

```{r}
# perform cross-validation for an MM regression model
fitLmrob <- lmrob(Y ~ ., data = coleman, k.max = 500)
cvFitLmrob <- cvLmrob(fitLmrob, cost = rtmspe,
folds = folds, trim = 0.1)
```

```{r}
# perform cross-validation for an LTS regression model
fitLts <- ltsReg(Y ~ ., data = coleman)
cvFitLts <- cvLts(fitLts, cost = rtmspe,
folds = folds, trim = 0.1)
```

```{r}
# combine results into one object
cvFits <- cvSelect(LS = cvFitLm, MM = cvFitLmrob, LTS = cvFitLts)
cvFits
# plot results for the MM regression model
plot(cvFitLmrob, method = "bw")
plot(cvFitLmrob, method = "density")
```

```{r}
# plot combined results
plot(cvFits, method = "bw")
plot(cvFits, method = "density")
plot(cvFits, method = "xy")
plot(cvFits, method = "dot")
## compare raw and reweighted LTS estimators for
## 50% and 75% subsets
```

```{r}# 50% subsets
fitLts50 <- ltsReg(Y ~ ., data = coleman, alpha = 0.5)
cvFitLts50 <- cvLts(fitLts50, cost = rtmspe, folds = folds,
fit = "both", trim = 0.1)
```

```{r}
# 75% subsets
fitLts75 <- ltsReg(Y ~ ., data = coleman, alpha = 0.75)
cvFitLts75 <- cvLts(fitLts75, cost = rtmspe, folds = folds,
fit = "both", trim = 0.1)
```

```{r}
# combine results into one object
cvFitsLts <- cvSelect("0.5" = cvFitLts50, "0.75" = cvFitLts75)
cvFitsLts
```

```{r}
# plot combined results
plot(cvFitsLts, method = "bw")
plot(cvFitsLts, method = "density")
plot(cvFitsLts, method = "xy")
plot(cvFitsLts, method = "dot")
```

#### Details 

For objects with multiple columns of cross-validation results, conditional plots are produced.

#### Value
An object of class "trellis" is returned invisibly. The update method can be used to update components of the object and the print method (usually called by default) will plot it on an appropriate plotting device.


#### Author(s)
Andreas Alfons
See Also
cvFit, cvSelect, cvTuning, bwplot, densityplot, xyplot, dotplot
