---
title: "``cvTools::subset.cv()``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(cvTools)
```

Subsetting cross-validation results

#### Description 

Extract subsets of results from (repeated) K-fold cross-validation.

#### Usage 
<pre><code>

## S3 method for class 'cv'
subset(x, select = NULL, ...)
## S3 method for class 'cvSelect'
subset(x, subset = NULL,
select = NULL, ...)

</code></pre>
#### Arguments 

* x an object inheriting from class "cv" or "cvSelect" that contains cross-validation results.
* subset a character, integer or logical vector indicating the subset of models for which to keep the cross-validation results.
* select a character, integer or logical vector indicating the columns of cross-validation results to be extracted.
* ... currently ignored.

#### Value
An object similar to x containing just the selected results.
Author(s)
Andreas Alfons
See Also
cvFit, cvSelect, cvTuning, subset

#### Examples 
```{r}

library("robustbase")
data("coleman")
set.seed(1234) # set seed for reproducibility
## set up folds for cross-validation
folds <- cvFolds(nrow(coleman), K = 5, R = 10)
## compare raw and reweighted LTS estimators for
## 50% and 75% subsets
# 50% subsets
fitLts50 <- ltsReg(Y ~ ., data = coleman, alpha = 0.5)
cvFitLts50 <- cvLts(fitLts50, cost = rtmspe, folds = folds,
fit = "both", trim = 0.1)
# 75% subsets
fitLts75 <- ltsReg(Y ~ ., data = coleman, alpha = 0.75)
cvFitLts75 <- cvLts(fitLts75, cost = rtmspe, folds = folds,
fit = "both", trim = 0.1)
# combine results into one object
cvFitsLts <- cvSelect("0.5" = cvFitLts50, "0.75" = cvFitLts75)
cvFitsLts
# extract reweighted LTS results with 50% subsets
subset(cvFitLts50, select = "reweighted")
subset(cvFitsLts, subset = c(TRUE, FALSE), select = "reweighted")
```
