---
title: "``is.distances``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(distances)
```

distances
Constructor for distance metric objects

##### Description
distances constructs a distance metric for a set of points. Currently, it only creates Euclidean dis-
tances. It can, however, create distances in any linear projection of Euclidean space. In other words,
Mahalanobis distances or normalized Euclidean distances are both possible. It is also possible to
give each dimension of the space different weights.

#### Usage

distances(data, id_variable = NULL, dist_variables = NULL,
normalize = NULL, weights = NULL)

#### Arguments
data a matrix or data frame containing the data points between distances should be
derived.
id_variable optional IDs of the data points. If id_variable is a single string and data is a
data frame, the corresponding column in data will be taken as IDs. That column
will be excluded from data when constructing distances (unless it is listed in
dist_variables). If id_variable is NULL, the IDs are set to 1:nrow(data).
Otherwise, id_variable must be of length nrow(data) and will be used di-
rectly as IDs.distances
3
dist_variables optional names of the columns in data that should be used when constructing
distances. If dist_variables is NULL, all columns will be used (net of eventual
column specified by id_variable). If data is a matrix, dist_variables must
be NULL.
normalize optional normalization of the data prior to distance construction. If normalize
is NULL or "none", no normalization will be done (effectively setting normalize
to the identity matrix). If normalize is "mahalanobize", normalization will be
done with var(data) (i.e., resulting in Mahalanobis distances). If normalize
is "studentize", normalization is done with the diagonal of var(data). If
normalize is a matrix, it will be used in the normalization. If normalize is a
vector, a diagonal matrix with the supplied vector as its diagonal will be used.
The matrix used for normalization must be positive-semidefinite.
weights optional weighting of the data prior to distance construction. If normalize is
NULL no weighting will be done (effectively setting weights to the identity ma-
trix). If weights is a matrix, that will be used in the weighting. If normalize is
a vector, a diagonal matrix with the supplied vector as its diagonal will be used.
The matrix used for weighting must be positive-semidefinite.

#### Details

Let x and y be two data points in data described by two vectors. distances uses the following
metric to derive the distance between x and y:
p
(x − y)N −0.5 W (N −0.5 ) 0 (x − y)
where N −0.5 is the Cholesky decomposition (lower triangular) of the inverse of the matrix speficied
by normalize, and W is the matrix speficied by weights.
When normalize is var(data) (i.e., using the "mahalanobize" option), the function gives (weighted)
Mahalanobis distances. When normalize is diag(var(data)) (i.e., using the "studentize" op-
tion), the function divides each column by its variance leading to (weighted) normalized Euclidean
distances. If normalize is the identity matrix (i.e., using the "none" or NULL option), the function
derives ordinary Euclidean distances.
Value
Returns a distances object.

#### Examples
```{r}
my_data_points <- data.frame(x = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10),
y = c(10, 9, 8, 7, 6, 6, 7, 8, 9, 10))
# Euclidean distances
my_distances1 <- distances(my_data_points)
# Euclidean distances in only one dimension
my_distances2 <- distances(my_data_points,
dist_variables = "x")4
distances
```

```{r}
# Mahalanobis distances
my_distances3 <- distances(my_data_points,
normalize = "mahalanobize")
# Custom normalization matrix
my_norm_mat <- matrix(c(3, 1, 1, 3), nrow = 2)
my_distances4 <- distances(my_data_points,
normalize = my_norm_mat)
# Give "x" twice the weight compared to "y"
my_distances5 <- distances(my_data_points,
weights = c(2, 1))

```

```{r}
# Use normalization and weighting
my_distances6 <- distances(my_data_points,
normalize = "mahalanobize",
weights = c(2, 1))
# Custom ID labels
my_data_points_withID <- data.frame(my_data_points,
my_ids = letters[1:10])
my_distances7 <- distances(my_data_points_withID,
id_variable = "my_ids")
```

```{r}
# Compare to standard R functions
all.equal(as.matrix(my_distances1), as.matrix(dist(my_data_points)))
# > TRUE
all.equal(as.matrix(my_distances2), as.matrix(dist(my_data_points[, "x"])))
# > TRUE
tmp_distances <- sqrt(mahalanobis(as.matrix(my_data_points),
unlist(my_data_points[1, ]),
var(my_data_points)))
names(tmp_distances) <- 1:10
all.equal(as.matrix(my_distances3)[1, ], tmp_distances)
# > TRUE
tmp_data_points <- as.matrix(my_data_points)
tmp_data_points[, 1] <- sqrt(2) * tmp_data_points[, 1]
all.equal(as.matrix(my_distances5), as.matrix(dist(tmp_data_points)))
# > TRUE
```

```{r}
tmp_data_points <- as.matrix(my_data_points)
tmp_cov_mat <- var(tmp_data_points)
tmp_data_points[, 1] <- sqrt(2) * tmp_data_points[, 1]
tmp_distances <- sqrt(mahalanobis(tmp_data_points,
tmp_data_points[1, ],
tmp_cov_mat))
names(tmp_distances) <- 1:10

all.equal(as.matrix(my_distances6)[1, ], tmp_distances)
# > TRUE
tmp_distances <- as.matrix(dist(my_data_points))
colnames(tmp_distances) <- rownames(tmp_distances) <- letters[1:10]
all.equal(as.matrix(my_distances7), tmp_distances)
# > TRUE

```
