---
title: "``nearest_neighbor_search``: Nearest neighbor search"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(distances)
```

#### Description
``nearest_neighbor_search`` searches for the k nearest neighbors of a set of query points.

#### Usage
<pre><code>
nearest_neighbor_search(distances, k, query_indices = NULL,
search_indices = NULL, radius = NULL)
</code></pre>

#### Arguments
* ``distances``: A distances object.
* ``k``: The number of neighbors to search for.
* ``query_indices``: An integer vector with point indices to query. If NULL, all data points in distances are queried.
* ``search_indices``: An integer vector with point indices to search among. If NULL, all data points in distances are searched over.
* ``radius``: Restrict the search to a fixed radius around each query. If fewer than k search
* ``points``: exist within this radius, no neighbors are reported (indicated by NA).



```{r}
nearest_neighbor_search(distances(iris[1:10,1:4]),3)
```

#### Value
A matrix with point indices for the nearest neighbors. Columns in this matrix indicate queries, and
rows are ordered by distances from the query.
