---
title: "``add_timestamps``:  Add timestamps to frames"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(moveVis)
```

#### Description
This function adds timestamps to animation frames created with ``frames_spatial``.

#### Usage
<pre><code>
add_timestamps(frames, m, x = NULL, y = NULL, ..., verbose = TRUE)
</code></pre>

#### Arguments 

* frames list of ggplot2 objects, crated with frames_spatial.
* m move or moveStack used to create frames with frames_spatial of uniform
* time scale and time lag, e.g. prepared with align_move.
* x numeric, optioanl, position of timestamps on the x scale. By default, timestamps
will be displayed in the top center.
* y numeric, optioanl, position of timestamps on the y scale.
* ... optional, arguments  passed to add_text, such as colour, size, type.
* verbose logical, if TRUE, messages on the function’s progress are displayed (default).

#### Examples
```{r}
library(moveVis)
library(move)
data("move_data", "basemap_data")
m <- align_move(move_data, res = 4, unit = "mins")
# create spatial frames using a custom NDVI base layer
r_list <- basemap_data[[1]]
r_times <- basemap_data[[2]]
frames <- frames_spatial(m, r_list = r_list, r_times = r_times, r_type = "gradient",
fade_raster = TRUE)
# add timestamps as text
frames.a <- add_timestamps(frames, m, type = "text")
frames.a[[100]]
# or use the ggplot2 "label" type:
frames.b <- add_timestamps(frames, m, type = "label")
frames.b[[100]]
```

Value
List of frames.
Author(s)
Jakob Schwalb-Willmann
See Also
frames_spatial frames_graph animate_frames
16 align_move
