---
title: "``add_northarrow``:  Add north arrow to frames"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(moveVis)
```

#### Description
This function adds a north arrow to the animation frames created with frames_spatial.

#### Usage

<pre><code>
add_northarrow(frames, height = 0.05, position = "bottomright",
x = NULL, y = NULL, colour = "black", size = 1,
label_text = "N", label_margin = 0.4, label_size = 5,
verbose = TRUE)
</code></pre>

#### Arguments 
frames list of ggplot2 objects, crated with frames_spatial.
height numeric, height of the north arrow in a range from 0 to 1 as the proportion of
the overall height of the frame map. Default is 0.5.
position character, position of the north arrow on the map. Either "bottomleft", "upperleft", "upperright", Ignored, if x and y are set.
x numeric, position of the bottom left corner of the north arrow on the x axis. If not set, position is used to calculate the position of the north arrow.
y numeric, position of the bottom left corner of the north arrow on the y axis. If not set, position is used to calculate the position of the north arrow.
* colour character, colour. Default is "black".
* size numeric, arrow size. Default is 1.
* label_text character, text below the north arrow. Default is "North".
* label_margin numeric, margin between label and north arrow as a proportion of the size of the north arrow. Default is 0.3.
label_size numeric, label font size. Default is 4.
* verbose logical, if TRUE, messages on the function’s progress are displayed (default).

#### Examples
```{r}
library(moveVis)
library(move)
data("move_data", "basemap_data")
m <- align_move(move_data, res = 4, unit = "mins")
# create spatial frames using a custom NDVI base layer
r_list <- basemap_data[[1]]
r_times <- basemap_data[[2]]
frames <- frames_spatial(m, r_list = r_list, r_times = r_times, r_type = "gradient",
fade_raster = TRUE)
# add a north arrow to frames:
add_progress 11
frames.a <- add_northarrow(frames)
frames.a[[100]]
# or in white at another position
frames.b <- add_northarrow(frames, colour = "white", position = "bottomleft")
frames.b[[100]]
```

Value
List of frames.
Author(s)
Jakob Schwalb-Willmann
See Also
frames_spatial frames_graph animate_frames
