---
title: "``add_text``:   Add static or dynamic text to frames"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(moveVis)
```


#### Description
This function adds static or dynamically changing text to the animation frames created with frames_spatial.

#### Usage
<pre><code>
add_text(frames, labels, x, y, colour = "black", size = 3,
type = "text", verbose = TRUE)
</code></pre>

#### Arguments 

* frames list of ggplot2 objects, crated with frames_spatial.
* labels character, text to be added to frames. Either a single character value or a character vector of same length as frames.
* x numeric, position of text on the x scale. Either a single numeric value or a numeric vector of same length as frames.
* y numeric, position of text on the y scale. Either a single numeric value or a numeric vector of same length as frames.
colour character, the text colour(s). Either a single character value or a character vector
of same length as frames.
* size numeric, the text size(s). Either a single numeric value or a numeric vector of
same length as frames.
* type character, either "text" to draw text or "label" to draw text inside a box.
* verbose logical, if TRUE, messages on the function’s progress are displayed (default).

#### Value
List of frames.
Author(s)
Jakob Schwalb-Willmann
See Also
frames_spatial frames_graph animate_frames
#### Examples
```{r}
library(moveVis)
library(move)
data("move_data", "basemap_data")
m <- align_move(move_data, res = 4, unit = "mins")
# create spatial frames using a custom NDVI base layer
r_list <- basemap_data[[1]]
r_times <- basemap_data[[2]]
frames <- frames_spatial(m, r_list = r_list, r_times = r_times, r_type = "gradient",
fade_raster = TRUE)
add_timestamps 15
# add text somewhere to all frames:
frames.a <- add_text(frames, "Water area", x = 8.959, y = 47.7305,
colour = "white", size = 3)
frames.a[[100]]
# or use the ggplot2 "label" type:
frames.b <- add_text(frames, "Water area", x = 8.959, y = 47.7305,
colour = "black", size = 3, type = "label")
frames.b[[100]]
```
