---
title: "``add_colourscale``:    Add scale to frames"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(moveVis)
```



#### Description
This function adjusts the colour scales of the animation frames created with frames_spatial and
custom map imagery.

#### Usage
add_colourscale(frames, type, colours, labels = waiver(),
legend_title = NULL, verbose = TRUE)

#### Arguments 
* frames list of ggplot2 objects, crated with frames_spatial.
type character, either "gradient" or "discrete". Must be equal to the defintion of argument r_type with which frames have been created (see frames_spatial).
* colours character, a vector of colours. If type = "discrete", number of colours must
be equal to the number of classes contained in the raster imagery with which frames have been created. Provide a named vector to associate map values with
colours, e.g. c("1" = "red", "2" = "green", "3" = "black")
labels character, a vector of labels with the same length as colours. Ignored, if
type = "gradient".
* legend_title character, a legend title.
* verbose logical, if TRUE, messages on the function’s progress are displayed (default).

#### Examples

```{r}
library(moveVis)
library(move)
data("move_data", "basemap_data")
# align movement
m <- align_move(move_data, res = 4, unit = "mins")
add_gg 5
# create spatial frames with frames_spatial:
r_list <- basemap_data[[1]]
r_times <- basemap_data[[2]]
frames <- frames_spatial(m, r_list = r_list, r_times = r_times, r_type = "gradient",
fade_raster = TRUE)
frames[[100]] # take a look at one of the frames
# default blue is boring, let's change the colour scale of all frames
frames <- add_colourscale(frames, type = "gradient", colours = c("orange", "white", "darkgreen"),
legend_title = "NDVI")
frames[[100]]
# let's make up some classification data with 10 classes
r_list <- lapply(r_list, function(x){
y <- raster::setValues(x, round(raster::getValues(x)*10))
return(y)
})
# turn fade_raster to FALSE, since it makes no sense to temporally interpolate discrete classes
frames <- frames_spatial(m, r_list = r_list, r_times = r_times, r_type = "discrete",
fade_raster = FALSE)
frames[[100]]
# now, let's assign a colour per class value to frames
colFUN <- colorRampPalette(c("orange", "lightgreen", "darkgreen"))
cols <- colFUN(10)
frames <- add_colourscale(frames, type = "discrete", colours = cols, legend_title = "Classes")
frames[[100]]
```

Value
List of frames.
Author(s)
Jakob Schwalb-Willmann
See Also
frames_spatial frames_graph animate_frames
