---
title: "``arsenal::compare.data.frame``"
2output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(arsenal)
```



Compare two data.frames and report differences

#### Description

Compare two data.frames and report any differences between them, much like SAS’s PROC COMPARE
procedure.

#### Usage
<pre><code>

## S3 method for class 'data.frame'
compare(x, y, by = NULL, by.x = by, by.y = by,
control = NULL, ...)
## S3 method for class 'compare.data.frame'
print(x, ...)

</code></pre>
#### Arguments

* x, y
A data.frame to compare
* by, by.x, by.y Which variables are IDs to merge the two data.frames? If set to "row.names",
merging will occur over the row.names. If set to NULL (default), merging will
occur row-by-row.
* control A list of control parameters from comparison.control.
* ... Other arguments, passed to comparison.control when appropriate.


Author(s)
Ethan Heinzen, adapted from code from Andrew Hanson
See Also
summary.compare.data.frame, n.diffs, n.diff.obs

#### Examples
```{r}
df1 <- data.frame(id = paste0("person", 1:3), a = c("a", "b", "c"),
b = c(1, 3, 4), c = c("f", "e", "d"),
row.names = paste0("rn", 1:3), stringsAsFactors = FALSE)
df2 <- data.frame(id = paste0("person", 3:1), a = c("c", "b", "a"),
b = c(1, 3, 4), d = paste0("rn", 1:3),
row.names = paste0("rn", c(1,3,2)), stringsAsFactors = FALSE)
summary(compare(df1, df2))
summary(compare(df1, df2, by = "id"))
summary(compare(df1, df2, by = "row.names"))
```
