---
title: "formulize"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(arsenal)
```
formulize
formulize

#### Description

A shortcut to generate one-, two-, or many-sided formulas from vectors of variable names.

#### Usage
<pre><code>

formulize(y = "", x = "", ..., data = NULL)

</code></pre>
#### Arguments

y, x, ... Character vectors, names, or calls to be collapsed (by "+") and put left-to-right
in the formula. If data is supplied, these can also be numeric, denoting which
column name to use. See examples.
data An R object with non-null column names.
Author(s)
Ethan Heinzen
See Also
reformulate

#### Examples
```{r}
## two-sided formula
formulize("y", c("x1", "x2", "x3"))
## one-sided formula
formulize(x = c("x1", "x2", "x3"))
## multi-sided formula
formulize("y", c("x1", "x2", "x3"), c("z1", "z2"), "w1")
## can use numerics for column names
data(mockstudy)
formulize(y = 1, x = 2:4, data = mockstudy)
```

```{r}
## mix and match
formulize(1, c("x1", "x2", "x3"), data = mockstudy)
## get an interaction
formulize("y", c("x1*x2", "x3"))
## no intercept
formulize("y", "x1 - 1")
formulize("y", c("x1", "x2", "-1"))
```

```{r}
## use in an lm
form <- formulize(2, 3:4, data = mockstudy)
summary(lm(form, data = mockstudy))
## using non-syntactic names or calls (like reformulate example)
formulize(as.name("+-"), c("`P/E`", "`% Growth`"))
f <- Surv(ft, case) ~ a + b
formulize(f[[2]], f[[3]])
```