
---
title: "``arsenal::freqlist``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(arsenal)
```


#### Description

Approximate the output from SAS’s PROC FREQ procedure when using the /list option of the
TABLE statement.

#### Usage
<pre><code>

freqlist(object, ...)
## S3 method for class 'table'
freqlist(object, na.options = c("include", "showexclude",
"remove"), strata = NULL, labelTranslations = NULL, control = NULL,...)
## S3 method for class 'formula'
freqlist(formula, data, subset, na.action,
strata = NULL, labelTranslations = NULL, control = NULL, addNA,
exclude, drop.unused.levels, ...)

</code></pre>
#### Arguments

* ``object``:  An R object, usually of class "table" or class "xtabs"
* ``... ``: additional arguments. In the formula method, these are passed to the table method. These are also passed to freq.control
na.options a character string indicating how to handling missing values: "include" (include values with NAs in counts and percentages), "showexclude" (show NAs
but exclude from cumulative counts and all percentages), "remove" (remove values with NAs); default is "include".
strata (formerly groupBy) an optional character string specifying a variable(s) to use for grouping when calculating cumulative counts and percentages. summary.freqlist
will also separate by grouping variable for printing. Note that this is different from modelsum and tableby, which take bare column names (and only one, at
that!)16
freqlist.internal
labelTranslations
an optional character string (or list) of labels to use for variable levels when summarizing. Names will be matched appropriately.
control: control parameters to handle optional settings within freqlist. See freq.control
formula, data, subset, na.action, addNA, exclude, drop.unused.levels

Arguments passed to xtabs. Note that addNA= only works in R >= 3.4.0.

#### Value

An object of class c("freqlist", "arsenal_table")
Author(s)
Tina Gunderson, with revisions by Ethan Heinzen
See Also
arsenal_table, summary.freqlist, freq.control, table, xtabs, kable

#### Examples
```{r}
# load mockstudy data
data(mockstudy)
tab.ex <- table(mockstudy[c("arm", "sex", "mdquality.s")], useNA = "ifany")
noby <- freqlist(tab.ex, na.options = "include")
summary(noby)
withby <- freqlist(tab.ex, strata = c("arm","sex"), na.options = "showexclude")
summary(withby)
```
