---
title: "``arsenal::mockstudy``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(arsenal)
```



Mock study data for examples

#### Description

Mock clinical study data for examples to test data manipulation and statistical functions. The function ``muck_up_mockstudy()`` is used in examples for ``compare.data.frame``.

#### Usage
<pre><code>

mockstudy
muck_up_mockstudy()
</code></pre>

#### Format
A data frame with 1499 observations on the following 15 variables:
case a numeric identifier-patient ID
* age age in years
* arm treatment arm divided into 3 groups, character string
* sex a factor with levels Male Female
* race self-reported race/ethnicity, character string
* fu.time survival or censoring time in years
* fu.stat censoring status; 1=censor, 2=death
* ps integer, ECOG performance score
* hgb numeric, hemoglobin count
* bmi numeric, body mass index, kg/m^2
* alk.phos numeric, alkaline phosphatase
* ast numeric, aspartate transaminase
* mdquality.s integer, LASA QOL 0=Clinically Deficient, 1=Not Clinically Deficient
* age.ord an ordered factor split of age, with levels 10-19 < 20-29 < 30-39 < 40-49 < 50-59 <
60-69 < 70-79 < 80-89

#### Examples
```{r}
data(mockstudy)
str(mockstudy)
```