---
title: "``arsenal::summary.freqlist``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(arsenal)
```



summary.freqlist

#### Description

Summarize the freqlist object.

#### Usage
<pre><code>

## S3 method for class 'freqlist'
summary(object, ..., labelTranslations = NULL,
title = NULL)
## S3 method for class 'summary.freqlist'
as.data.frame(x, ..., list.ok = FALSE)

</code></pre>
#### Arguments

object
an object of class freqlist
...
For summary.freqlist, these are passed to as.data.frame.freqlist (and
hence to freq.control). For the print method, these are additional arguments
passed to the kable function.
labelTranslations
A named list (or vector) where the name is the label in the output to be replaced
in the pretty rendering by the character string value for the named element of
the list, e.g., list(age = "Age(Years)", meansd = "Mean(SD)").
title Title for the table, defaulting to NULL (no title)
x An object of class summary.freqlist.
list.ok If the object has multiple by-variables, is it okay to return a list of data.frames
instead of a single data.frame? If FALSE but there are multiple by-variables, a
warning is issued.

#### Value

An object of class "summary.freqlist" (invisibly for the print method).summary.modelsum
33
Author(s)
Tina Gunderson, with major revisions by Ethan Heinzen
See Also
freqlist, table, xtabs, kable

#### Examples
```{r}
# load mockstudy data
data(mockstudy)
tab.ex <- table(mockstudy[c("arm", "sex", "mdquality.s")], useNA = "ifany")
noby <- freqlist(tab.ex, na.options = "include")
summary(noby)
withby <- freqlist(tab.ex, strata = c("arm","sex"), na.options = "showexclude")
summary(withby)
summary(withby, dupLabels = TRUE)
```
