---
title: "arsenal::write2"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(arsenal)
```
write2

#### Description

Functions to output tables to a single document. (Also the S3 backbone behind the write2* functions.)

#### Usage
<pre><code>

write2(object, file, ..., output_format)
## S3 method for class 'arsenal_table'
write2(object, file, ..., output_format = NULL)
## S3 method for class 'summary.arsenal_table'
write2(object, file, ...,
output_format = NULL)
## S3 method for class 'compare.data.frame'
write2(object, file, ...,
output_format = NULL)
## S3 method for class 'summary.compare.data.frame'
write2(object, file, ...,
output_format = NULL)
## S3 method for class 'verbatim'
write2(object, file, ..., output_format = NULL)
## S3 method for class 'yaml'
write2(object, file, ..., output_format = NULL)
## S3 method for class 'code.chunk'
write2(object, file, ..., output_format = NULL)
## S3 method for class 'knitr_kable'
write2(object, file, ..., output_format = NULL)
## S3 method for class 'xtable'
write2(object, file, ..., output_format = NULL)46
write2
## S3 method for class 'character'
write2(object, file, ..., output_format = NULL)
## S3 method for class 'list'
write2(object, file, ..., append. = FALSE,
render. = TRUE, keep.rmd = !render., output_format = NULL)
## Default S3 method:
write2(object, file, FUN = NULL, ...,
append. = FALSE, render. = TRUE, keep.rmd = !render.,
output_format = NULL)

</code></pre>
#### Arguments

object An object.
file A single character string denoting the filename for the output document.
... Additional arguments to be passed to FUN, rmarkdown::render, etc. One pop-
ular option is to use quiet = TRUE to suppress the command line output.
output_format One of the following:
1. An output format object, e.g. rmarkdown::html_document(...).
2. A character string denoting such a format function, e.g. "html_document".
In this case, the "..." are NOT passed.
3. The format function itself, e.g. rmarkdown::html_document. In this case,
the "..." arguments are passed.
4. One of "html", "pdf", and "word", shortcuts implemented here. In this
case, the "..." arguments are passed.
5. NULL, in which the output is HTML by default.
See rmarkdown::render for details.
append. Logical, denoting whether (if a temporary .Rmd file of the same name already
exists) to append on. Used mostly for write2.list.
render. Logical, denoting whether to render the temporary .Rmd file. Used mostly for
write2.list.
keep.rmd Logical, denoting whether to keep the intermediate .Rmd file. Used mostly for
write2.list.
FUN The summary-like or print-like function to use to generate the markdown con-
tent. Can be passed as a function or a character string. It’s expected that
FUN(object, ...) looks "good" when put directly in a .Rmd file.

#### Examples
```{r}
## Not run:
data(mockstudy)
# tableby example
tab1 <- tableby(arm ~ sex + age, data=mockstudy)
write2(tab1, tempfile(fileext = ".rtf"),
toc = TRUE, # passed to rmarkdown::rtf_document, though in this case it's not practical
quiet = TRUE, # passed to rmarkdown::render
title = "My cool new title", # passed to summary.tableby
output_format = rmarkdown::rtf_document)
## End(Not run)
write2html(list(
"# Header 1", # a header
code.chunk(a <- 1, b <- 2, a + b), # a code chunk
verbatim("hi there") # verbatim output
),
tempfile(fileext = ".html"),
quite = TRUE)
```

Details
write2 is an S3 method. The default prints the object (using print) inside a section surrounded by three back ticks. See verbatim for details.
There are methods implemented for tableby, modelsum, and freqlist, all of which use the summary function. There are also methods compatible with kable, xtable, and pander_return.write2.internal
47
Another option is to coerce an object using verbatim() to print out the results monospaced (as if they were in the terminal). To output multiple tables into a document, simply make a list of them and
call the same function as before. Finally, to output code chunks to be evaluated, use code.chunk.
For more information, see vignette("write2").

#### Value

object is returned invisibly, and file is written.
Author(s)
Ethan Heinzen, adapted from code from Krista Goergen
See Also
write2word, write2pdf, write2html, render, word_document, html_document, pdf_document,
rtf_document, md_document, odt_document
