---
title: "``arsenal::write2specific``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(arsenal)
```
write2specific
write2word, write2html, write2pdf

#### Description

Functions to output tables to a single Word, HTML, or PDF document.

#### Usage
<pre><code>

write2word(object, file, ...)
write2pdf(object, file, ...)
write2html(object, file, ...)write2specific
49

</code></pre>
#### Arguments

object An object.
file A single character string denoting the filename for the output document.
... Additional arguments to be passed to FUN, rmarkdown::render, etc. One pop-
ular option is to use quiet = TRUE to suppress the command line output.
Details
To generate the appropriate file type, the write2* functions use one of rmarkdown::word_document,
rmarkdown::html_document, and rmarkdown::pdf_document to get the job done. "..." argu-
ments are passed to these functions, too.

#### Value

object is returned invisibly, and file is written.
Author(s)
Ethan Heinzen, adapted from code from Krista Goergen
See Also
write2

#### Examples
```{r}
## Not run:
data(mockstudy)
# tableby example
tab1 <- tableby(arm ~ sex + age, data=mockstudy)
write2html(tab1, "~/trash.html")
# freqlist example
tab.ex <- table(mockstudy[, c("arm", "sex", "mdquality.s")], useNA = "ifany")
noby <- freqlist(tab.ex, na.options = "include")
write2pdf(noby, "~/trash2.pdf")
# A more complicated example
write2word(tab1, "~/trash.doc",
keep.md = TRUE,
reference_docx = mystyles.docx, # passed to rmarkdown::word_document
quiet = TRUE, # passed to rmarkdown::render
title = "My cool new title") # passed to summary.tableby
## End(Not run)
```
