---
title: "``a3.lm``: A3 for Linear Regressions"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(A3)
```


#### Description
This convenience function calculates the A3 results specifically for linear regressions. It uses R's glm function and so supports logistic regressions and other link functions using the family argument.
For other forms of models you may use the more general a3 function.

#### Usage 

<pre><code>
a3.lm(formula, data, family = gaussian, ...)
</code></pre>

#### Arguments 
* ``formula``: the regression formula.
* ``data``: a data frame containing the data to be used in the model fit.
* ``family``: the regression family. Typically 'gaussian' for linear regressions.
* ``...``: additional arguments  passed to a3.base.


#### Examples 
```{r}
## Standard linear regression results:
summary(lm(rating ~ ., attitude))
## A3 linear regression results:
# In practice, p.acc should be <= 0.01 in order
# to obtain fine grained p values.
a3.lm(rating ~ ., attitude, p.acc = 0.1)
# This is equivalent both to:
a3(rating ~ ., attitude, glm, model.args = list(family = gaussian), p.acc = 0.1)
# and also to:
a3(rating ~ ., attitude, lm, p.acc = 0.1)
```
#### Value
S3 A3 object; see a3.base for details