---
title: "a3"
author: "Kevin O'Brien"
date: "25 December 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
a3 A3 Results for Arbitrary Model
#### Description
This function calculates the A3 results for an arbitrary model construction algorithm (e.g. Linear
Regressions, Support Vector Machines or Random Forests). For linear regression models, you may
use the a3.lm convenience function.
#### Usage 
<pre><code>
a3(formula, data, model.fn, model.args = list(), ...)
</code></pre>

#### Arguments 
formula the regression formula.
data a data frame containing the data to be used in the model fit.
model.fn the function to be used to build the model.
model.args a list of arguments  passed to model.fn.
... additional arguments  passed to a3.base.

#### Value
S3 A3 object; see a3.base for details
#### References
Scott Fortmann-Roe (2015). Consistent and Clear Reporting of Results from Diverse Modeling
Techniques: The A3 Method. Journal of Statistical Software, 66(7), 1-23. <http://www.jstatsoft.org/v66/i07/>

#### Examples 
```{r}
## Standard linear regression results:
summary(lm(rating ~ ., attitude))
## A3 Results for a Linear Regression model:
# In practice, p.acc should be <= 0.01 in order
# to obtain finer grained p values.
a3(rating ~ ., attitude, lm, p.acc = 0.1)
## A3 Results for a Random Forest model:
# It is important to include the "+0" in the formula to eliminate the constant term.

```


```{r}
require(randomForest)
a3(rating ~ .+0, attitude, randomForest, p.acc = 0.1)
# Set the ntrees argument of the randomForest function to 100
a3(rating ~ .+0, attitude, randomForest, p.acc = 0.1, model.args = list(ntree = 100))
# Speed up the calculation by doing 5-fold cross-validation.
# This is faster and more conservative (i.e. it should over-estimate error)
a3(rating ~ .+0, attitude, randomForest, n.folds = 5, p.acc = 0.1)
# Use Leave One Out Cross Validation. The least biased approach but, for large data sets, potentially very slow.
```


```{r}
a3(rating ~ .+0, attitude, randomForest, n.folds = 0, p.acc = 0.1)
## Use a Support Vector Machine algorithm.
# Just calculate the slopes and R^2 values, do not calculate p values.
require(e1071)
a3(rating ~ .+0, attitude, svm, p.acc = NULL)
```





