``cartogram_cont`` Calculate Contiguous Cartogram Boundaries

#### Description
Construct a continuous area cartogram by a rubber sheet distortion algorithm (Dougenik et al. 1985)

#### Usage
<pre><code>
cartogram_cont(x, weight, itermax = 15, maxSizeError = 1.0001, prepare = "adjust", threshold = 0.05)

## S3 method for class 'SpatialPolygonsDataFrame'
cartogram_cont(x, weight, itermax = 15, maxSizeError = 1.0001, prepare = "adjust", threshold = 0.05)

## S3 method for class 'sf'
cartogram_cont(x, weight, itermax = 15, maxSizeError = 1.0001, prepare = "adjust", threshold = 0.05)
</code></pre>

#### Arguments
* ``x``: SpatialPolygonDataFrame or an sf object
* ``weight``: Name of the weighting variable in x
* ``itermax``: Maximum iterations for the cartogram transformation, if maxSizeError ist not reached
* ``maxSizeError``: Stop if meanSizeError is smaller than maxSizeError
* ``prepare``: Weighting values are adjusted to reach convergence much earlier. Possible methods are "adjust", adjust values to restrict the mass vector to the quantiles defined by threshold and 1-threshold (default), "remove", remove features with values
lower than quantile at threshold, "none", don’t adjust weighting values threshold Define threshold for data preparation


#### Examples

```{r}
library(maptools)
library(cartogram)
library(rgdal)
data(wrld_simpl)
# Remove uninhabited regions
```

```{r}
afr <- spTransform(wrld_simpl[wrld_simpl$REGION==2 & wrld_simpl$POP2005 > 0,],
CRS("+init=epsg:3395"))
# Create cartogram
afr_carto <- cartogram_cont(afr, "POP2005", 3)
```

```{r}
# Plot
par(mfcol=c(1,2))
plot(afr, main="original")
plot(afr_carto, main="distorted (sp)")
```

```{r}
# Same with sf objects
library(sf)
afr_sf = st_as_sf(afr)
afr_sf_carto <- cartogram_cont(afr_sf, "POP2005", 3)
```

```{r}
# Plot
par(mfcol=c(1,3))
plot(afr, main="original")
plot(afr_carto, main="distorted (sp)")
plot(st_geometry(afr_sf_carto), main="distorted (sf)")
```

#### Value
An object of the same class as x
References
Dougenik, J. A., Chrisman, N. R., & Niemeyer, D. R. (1985). An Algorithm To Construct Continuous
Area Cartograms. In The Professional Geographer, 37(1), 75-81.
cartogram_dorling 3
