cartogram_dorling Calculate Non-Overlapping Circles Cartogram

#### Description
Construct a cartogram which represents each geographic region as non-overlapping circles (Dorling
1996).

#### Usage
<pre><code>
cartogram_dorling(x, weight, k = 5, m_weight = 1, itermax = 1000)
## S3 method for class 'sf'
cartogram_dorling(x, weight, k = 5, m_weight = 1, itermax = 1000)

## S3 method for class 'SpatialPolygonsDataFrame'
cartogram_dorling(x, weight, k = 5, m_weight = 1, itermax = 1000)

</code></pre>

#### Arguments
* ``x``: SpatialPolygonsDataFrame, SpatialPointsDataFrame or an sf object
* ``weight``: Name of the weighting variable in x
* ``k``: Share of the bounding box of x filled by the larger circle
* ``m_weight``: Circles’ movements weights. An optional vector of numeric weights (0 to 1 inclusive) to apply to the distance each circle moves during pair-repulsion. A weight of 0 prevents any movement. A weight of 1 gives the default movement
distance. A single value can be supplied for uniform weights. A vector with length less than the number of circles will be silently extended by repeating the final value. Any values outside the range [0, 1] will be clamped to 0 or 1.
* ``itermax``: Maximum iterations for the cartogram transformation.

#### Value
Non overlaping proportional circles of the same class as x.
References
Dorling, D. (1996). Area Cartograms: Their Use and Creation. In Concepts and Techniques in
Modern Geography (CATMOG), 59.

#### Examples
```{r}
library(maptools)
library(cartogram)
library(rgdal)
data(wrld_simpl)
# Remove uninhabited regions
afr <- spTransform(wrld_simpl[wrld_simpl$REGION==2 & wrld_simpl$POP2005 > 0,],
CRS("+init=epsg:3395"))
```

```{r}
# Create cartogram
afr_carto <- cartogram_dorling(afr, "POP2005")
# Plot
par(mfcol=c(1,2))
plot(afr, main="original")
plot(afr, main="distorted (sp)")
plot(afr_carto, col = "red", add=TRUE)
```

```{r}
# Same with sf objects
library(sf)
cartogram_ncont 5
afr_sf = st_as_sf(afr)
afr_sf_carto <- cartogram_dorling(afr_sf, "POP2005")
```

```{r}
# Plot
par(mfcol=c(1,3))
plot(afr, main="original")
plot(afr_carto, main="distorted (sp)")
plot(st_geometry(afr_sf_carto), main="distorted (sf)")
```
