---
title: "abodOutlier"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(abodOutlier)
```
Package 'abodOutlier'
August 29, 2016

#### Title Angle-Based Outlier Detection
Version 0.1
Author Jose Jimenez <jose@jimenezluna.com>
Maintainer Jose Jimenez <jose@jimenezluna.com>

#### Description 

Performs angle-based outlier detection on a given dataframe. Three methods are available, a full but slow implementation using all the data that has cubic complexity, a fully randomized one which is way more efficient and another using k-nearest neighbours. These algorithms are specially well suited for high dimensional data outlier detection.

* Depends cluster, R (>= 3.1.2)
* License MIT + file LICENSE
* LazyData true
* Encoding UTF-8
* NeedsCompilation no
* Repository CRAN
* Date/Publication 2015-08-31 14:31:42

#### Topics documented:
abod 
abodoutlier 




abod Angle-Based Outlier Factor
#### Description
Computes angle-based outlier factor for each observation in the dataset

#### Usage
<pre><code>
abod(data, method = "complete", n_sample_size = trunc(nrow(data)/10), k = 15)
</code></pre>

#### Arguments
* ``data`` Dataframe in which to compute angle-based outlier factor.
* ``method`` Method to perform. 'complete' will use the entire dataset (cubic complexity) to compute abof. 'randomized' will use a random sample of the data of size '``n_sample_size``'. 'knn' will compute abof among '``k``' nearest neighbours.
* ``n_sample_size`` Number of random observations to choose in randomized method.
* ``k`` Number of nearest neighbours to choose in knn method.

#### Details
Please note that 'knn' has to compute an euclidean distance matrix before computing abof.


#### Examples
```{r}
abod(faithful, method = "randomized", n_sample_size = 5)
abod(faithful, method = "knn", k = 5)
```

#### Value

Returns angle-based outlier factor for each observation. A small ***abof*** respect the others would
indicate presence of an outlier.
#### Author(s)
Jose Jimenez <jose@jimenezluna.com>

#### References
[1] Angle-Based Outlier Detection in High-dimensional Data. KDD 2008. Hans-Peter Kriegel,
Matthias Schubert, Arthur Zimek. (http://www.dbs.ifi.lmu.de/Publikationen/Papers/KDD2008.pdf)



abodoutlier Angle-based outlier detection
abodoutlier 3
Description
Performs angle-based outlier detection on data. A complete, a randomized and a knn based methods
are available.
Package: abodoutlier
Type: Package
Version: 0.1
Date: 2015-08-30
License: MIT License
Maintainer: Jose Jimenez <jose@jimenezluna.com>
