Package 'DCG'
June 8, 2016
Type Package
Title Data Cloud Geometry (DCG): Using Random Walks to Find Community
Structure in Social Network Analysis
Version 0.9.2
Date 2016-05-09
Depends R (>= 2.14.0)

#### Description 
 Data cloud geometry (DCG) applies random walks in finding community structures
for social networks.
License GPL (>= 2)
Copyright Fushing Lab & McCowan Lab, University of California, Davis
Imports stats
LazyData TRUE
Suggests testthat, knitr, rmarkdown, devtools, lattice, png
RoxygenNote 5.0.1
VignetteBuilder knitr
NeedsCompilation no
Author Chen Chen [aut],
Jian Jin [aut, cre],
Brianne Beisner [aut],
Brenda McCowan [aut, cph],
Hsieh Fushing [aut, cph]
Maintainer Jian Jin <jinjian.pku@gmail.com>
Repository CRAN
Date/Publication 2016-06-08 05:47:08
R topics documented:
as.SimilarityMatrix....... . . 2
as.symmetricAdjacencyMatrix...... . 3
getEigenvalueList....... . . . 4
1
2 as.SimilarityMatrix
getEns........4
getEnsList........ . . 5
GetSim........ . . . 6
monkeyGrooming....... . . . 7
plotCLUSTERS.......7
plotMultiEigenvalues....... . 8
plotTheCluster.......10
temperatureSample....... . . 10
Index 12
as.SimilarityMatrix Convert a matrix to a similarity matrix. as.SimilarityMatrix convert
an adjacency matrix to a similarity matrix.

#### Description 

Convert a matrix to a similarity matrix. as.SimilarityMatrix convert an adjacency matrix to a
similarity matrix.
Usage
as.SimilarityMatrix(mat)

#### Arguments 

mat a symmetric adjacency matrix

#### Value 

a similarity matrix.

#### Examples 
```{r}

symmetricMatrix <- as.symmetricAdjacencyMatrix(monkeyGrooming, weighted = TRUE, rule = "weak")
similarityMatrix <- as.SimilarityMatrix(symmetricMatrix)
as.symmetricAdjacencyMatrix 3
as.symmetricAdjacencyMatrix
convert to a symmetric adjacency matrix

#### Description 

as.symmetricAdjacencyMatrix convert an edgelist or a raw matrix to a symmetric adjacency
matrix.
Usage
as.symmetricAdjacencyMatrix(Data, weighted = FALSE, rule = "weak")

#### Arguments 

Data either a dataframe or a matrix, representing raw interactions using either an
edgelist or a matrix. Frequency of interactions for each dyad can be represented
either by multiple occurrences of the dyad for a 2-column edgelist, or by a third
column specifying the frequency of the interaction for a 3-column edgelist.
weighted If the edgelist is a 3-column edgelist in which weight was specified by frequency,
use weighted = TRUE.
rule a character vector of length 1, being one of "weak", "strong", "upper", or
"lower". Ways of symmetrizing the matrix. See 
#### Details
 for more information.

#### Details

There are ways of symmetrizing a matrix. The "weak" rule symmetrize the matrix by building an
edge between nodes [i, j] and [j, i] if there is an edge either from i to j OR from j to i. The
"strong" rule symmetrize the matrix by building an edge between nodes [i, j] and [j, i] if
there is an edge BOTH from i to j AND from j to i. The "upper" and the "lower" rule symmetrize
the matrix by using the "upper" or the "lower" triangle respectively.
Note, when using a 3-column edgelist (e.g. a weighted edgelist) to represent raw interactions, each
dyad must be unique. If more than one rows are found with the same Initiator and recipient, sum
of the frequencies will be taken to represent the freqency of interactions between this unique dyad.
A warning message will prompt your attention to the accuracy of your raw data when duplicated
dyads were found in a three-column edgelist.

#### Value 

a named matrix with the [i,j]th entry equal to the number of times i grooms j.

#### Examples 
```{r}

symmetricMatrix <- as.symmetricAdjacencyMatrix(monkeyGrooming, weighted = TRUE, rule = "weak")
```

getEigenvalueList generate eigenvalues for all ensemble matrices getEigenvalueList
get eigenvalues from ensemble matrices

#### Description 

generate eigenvalues for all ensemble matrices getEigenvalueList get eigenvalues from ensemble
matrices
Usage
getEigenvalueList(EnsList)

#### Arguments 

EnsList a list of ensemble matrices

#### Value 

a list of eigenvalues for each of the ensemble matrix in the ensemble matrices list.
getEns generate ensemble matrix getEns get ensemble matrix from given similarity
matrix and temperature

#### Description 

generate ensemble matrix getEns get ensemble matrix from given similarity matrix and temperature
Usage
getEns(simMat, temperature, MaxIt = 1000, m = 5)

#### Arguments 

simMat a similarity matrix
temperature a numeric vector of length 1, indicating the temperature used to transform the
similarity matrix to ensemble matrix
MaxIt number of iterations for regulated random walks
m maxiumnum number of time a node can be visited during random walks

#### Details

This function involves two steps. It first generate similarity matrices of different variances by taking
the raw similarity matrix to the power of each temperature. Then it called the function EstClust to
perform random walks in the network to identify clusters.
getEnsList 5

#### Value 

a matrix.
getEnsList generating a list of ensemble matrices based on the similarity matrix
and temperatures

#### Description 

getEnsList get ensemble matrices from given similarity matrix at all temperatures
Usage
getEnsList(simMat, temperatures, MaxIt = 1000, m = 5)

#### Arguments 

simMat a similarity matrix
temperatures temperatures selected
MaxIt number of iterations for regulated random walks
m maxiumnum number of time a node can be visited during random walks

#### Details

This step is crucial in finding community structure based on the similarity matrix of the social
network. For each temperatures, the similarity matrix was taken to the power of temperature as
saved as a new similarity matrix. This allows the random walk to explore the similarity matrix at
various variations. Random walks are then performed in similarity matrices of various temperatures.
In order to prevent random walks being stucked in a locale, the parameter m was set (to 5 by default)
to remove a node after m times of visits of the node. An ensemble matrix is generated at each
temperature in which values represent likelihood of two nodes being in the same community.

#### Value 

a list of ensemble matrices

#### References 

Fushing, H., & McAssey, M. P. (2010). Time, temperature, and data cloud geometry. Physical
Review E, 82(6), 061110.
Chen, C., & Fushing, H. (2012). Multiscale community geometry in a network and its application.
Physical Review E, 86(4), 041120.
Fushing, H., Wang, H., VanderWaal, K., McCowan, B., & Koehl, P. (2013). Multi-scale clustering
by building a robust and self correcting ultrametric topology on data points. PloS one, 8(2), e56259.
6 GetSim

#### Examples 
```{r}

symmetricMatrix <- as.symmetricAdjacencyMatrix(monkeyGrooming, weighted = TRUE, rule = "weak")
Sim <- as.SimilarityMatrix(symmetricMatrix)
temperatures <- temperatureSample(start = 0.01, end = 20, n = 20, method = 'random')
## Not run:
# Note: It takes a while to run the getEnsList example.
Ens_list <- getEnsList(Sim, temperatures, MaxIt = 1000, m = 5)
## End(Not run)
```

GetSim GetSim get similarity matrix from a distance matrix

#### Description 

GetSim get similarity matrix from a distance matrix
Usage
GetSim(D, T)

#### Arguments 

D A distance matrix
T Temperature. temperatureSample

#### Details

the similarity matrix is calculated at each temperature T.

#### References 

Fushing, H., & McAssey, M. P. (2010). Time, temperature, and data cloud geometry. Physical
Review E, 82(6), 061110.
Chen, C., & Fushing, H. (2012). Multiscale community geometry in a network and its application.
Physical Review E, 86(4), 041120.
Fushing, H., Wang, H., VanderWaal, K., McCowan, B., & Koehl, P. (2013). Multi-scale clustering
by building a robust and self correcting ultrametric topology on data points. PloS one, 8(2), e56259.
monkeyGrooming 7
monkeyGrooming Grooming network data

#### Description 

A dataset containing grooming edgelist among monkeys.
Usage
monkeyGrooming
Format
A data frame with 1595 rows and 2 variables:
Initiator Grooming Initiator ID
Recipient Grooming Recipient ID
Groom Grooming Frequency ...
plotCLUSTERS generate tree plots for each ensemble matrix plotCLUSTERS plot all
cluster trees

#### Description 

generate tree plots for each ensemble matrix plotCLUSTERS plot all cluster trees
Usage
plotCLUSTERS(EnsList, mfrow, mar = c(1, 1, 1, 1), line = -1.5, cex = 0.5,
...)

#### Arguments 

EnsList a list in which elements are ensemble matrices.
mfrow A vector of the form c(nr, nc) passed to par.
mar plotting parameters with useful defaults (par)
line plotting parameters with useful defaults (par)
cex plotting parameters with useful defaults (par)
... further plotting parameters
8 plotMultiEigenvalues

#### Details

plotCLUSTERS plots all cluster trees with each tree corresponding to each ensemble matrix in the
list of ens_list. EnsList is the output from getEnsList.
mfrow determines the arrangement of multiple plots. It takes the form of c(nr, nc) with the first
parameter being the number of rows and the second parameter being the number of columns. When
deciding parameters for mfrow, one should take into considerations size of the plotting device and
number of cluster plots. For example, there are 20 cluster plots, mfrow can be set to c(4, 5) or
c(2, 10) depending on the size and shape of the plotting area.

#### Value 

a graph containing all tree plots with each tree plot corresponding to the community structure from
each of the ensemble matrix.

#### References 

Fushing, H., & McAssey, M. P. (2010). Time, temperature, and data cloud geometry. Physical
Review E, 82(6), 061110.
Chen, C., & Fushing, H. (2012). Multiscale community geometry in a network and its application.
Physical Review E, 86(4), 041120.
Fushing, H., Wang, H., VanderWaal, K., McCowan, B., & Koehl, P. (2013). Multi-scale clustering
by building a robust and self correcting ultrametric topology on data points. PloS one, 8(2), e56259.
See Also
getEnsList

#### Examples 
```{r}

symmetricMatrix <- as.symmetricAdjacencyMatrix(monkeyGrooming, weighted = TRUE, rule = "weak")
Sim <- as.SimilarityMatrix(symmetricMatrix)
temperatures <- temperatureSample(start = 0.01, end = 20, n = 20, method = 'random')
## Not run:
# for illustration only. skip CRAN check because it ran forever.
Ens_list <- getEnsList(Sim, temperatures, MaxIt = 1000, m = 5)
## End(Not run)
plotCLUSTERS(EnsList = Ens_list, mfrow = c(2, 10), mar = c(1, 1, 1, 1))
plotMultiEigenvalues plot eigenvalues plotMultiEigenvalues plot eigenvalues to determine
number of communities by finding the elbow point

#### Description 

plot eigenvalues plotMultiEigenvalues plot eigenvalues to determine number of communities by
finding the elbow point
plotMultiEigenvalues 9
Usage
plotMultiEigenvalues(Ens_list, mfrow, mar = c(2, 2, 2, 2), line = -1.5,
cex = 0.5, ...)

#### Arguments 

Ens_list a list in which elements are numeric vectors representing eigenvalues.
mfrow A vector of the form c(nr, nc) passed to par.
mar plotting parameters with useful defaults (par)
line plotting parameters with useful defaults (par)
cex plotting parameters with useful defaults (par)
... further plotting parameters

#### Details

plotMultiEigenvalues plot multiple eigenvalue plots. The dark blue colored dots indicate eigenvalue
greater than 0. Each of the ensemble matrices is decomposed into eigenvalues which is used
to determine appropriate number of communities. Plotting out eigenvalues allow us to see where
the elbow point is. The curve starting from the elbow point flatten out. The number of points above
(excluding) the elbow point indicates number of communities.
mfrow determines the arrangement of multiple plots. It takes the form of c(nr, nc) with the first
parameter being the number of rows and the second parameter being the number of columns. When
deciding parameters for mfrow, one should take into considerations size of the plotting device and
number of plots. For example, there are 20 plots, mfrow can be set to c(4, 5) or c(2, 10)
depending on the size and shape of the plotting area.

#### Value 

a pdf file in the working directory containing all eigenvalue plots

#### References 

Fushing, H., & McAssey, M. P. (2010). Time, temperature, and data cloud geometry. Physical
Review E, 82(6), 061110.
Chen, C., & Fushing, H. (2012). Multiscale community geometry in a network and its application.
Physical Review E, 86(4), 041120.
Fushing, H., Wang, H., VanderWaal, K., McCowan, B., & Koehl, P. (2013). Multi-scale clustering
by building a robust and self correcting ultrametric topology on data points. PloS one, 8(2), e56259.
See Also
plotCLUSTERS, getEnsList
10 temperatureSample

#### Examples 
```{r}

symmetricMatrix <- as.symmetricAdjacencyMatrix(monkeyGrooming, weighted = TRUE, rule = "weak")
Sim <- as.SimilarityMatrix(symmetricMatrix)
temperatures <- temperatureSample(start = 0.01, end = 20, n = 20, method = 'random')
## Not run:
# for illustration only. skip CRAN check because it ran forever.
Ens_list <- getEnsList(Sim, temperatures, MaxIt = 1000, m = 5)
## End(Not run)
```

plotMultiEigenvalues(Ens_list = Ens_list, mfrow = c(10, 2), mar = c(1, 1, 1, 1))
plotTheCluster generate tree plots for selected ensemble matrix plotTrees plot one
cluster tree

#### Description 

generate tree plots for selected ensemble matrix plotTrees plot one cluster tree
Usage
plotTheCluster(EnsList, index, ...)

#### Arguments 

EnsList a list in which elements are ensemble matrices.
index an integer. index of which ensemble matrix you want to plot.
... plotting parameters passed to par.

#### Value 

a tree plot
temperatureSample generate temperatures temperatureSample generate tempatures
based on either random or fixed intervals

#### Description 

generate temperatures temperatureSample generate tempatures based on either random or fixed
intervals
temperatureSample 11
Usage
temperatureSample(start = 0.01, end = 20, n = 20, method = "random")

#### Arguments 

start a numeric vector of length 1, indicating the lowest temperature
end a numeric vector of length 1, indicating the highest temperature
n an integer between 10 to 30, indicating the number of temperatures (more explanations
on what temperatures are).
method a character vector indicating the method used in selecting temperatures. It
should take either 'random' or 'fixedInterval', case-sensitive.

#### Details

In using random walks to find community structure, each normalized similarity matrix is evaluated
at different temperatures. This allows greater variations in the normalized similarity matrices. It is
recommended to try out 20 - 30 temperatures to allow for a thorough exploration of the matrices. A
range of temperatures which lead to stable community structures should be considered as reliable.
The temperature in the middle of the range should be selected.

#### Value 

a numeric vector of length n representing temperatures sampled.

#### References 

Fushing, H., & McAssey, M. P. (2010). Time, temperature, and data cloud geometry. Physical
Review E, 82(6), 061110.
Chen, C., & Fushing, H. (2012). Multiscale community geometry in a network and its application.
Physical Review E, 86(4), 041120.
Fushing, H., Wang, H., VanderWaal, K., McCowan, B., & Koehl, P. (2013). Multi-scale clustering
by building a robust and self correcting ultrametric topology on data points. PloS one, 8(2), e56259.
See Also
getEnsList

#### Examples 
```{r}

symmetricMatrix <- as.symmetricAdjacencyMatrix(monkeyGrooming, weighted = TRUE, rule = "weak")
Sim <- as.SimilarityMatrix(symmetricMatrix)
temperatures <- temperatureSample(start = 0.01, end = 20, n = 20, method = 'random')
Index
Topic datasets
monkeyGrooming, 7
as.SimilarityMatrix, 2
as.symmetricAdjacencyMatrix, 3
getEigenvalueList, 4
getEns, 4
getEnsList, 5, 8, 9, 11
GetSim, 6
monkeyGrooming, 7
par, 7, 9, 10
plotCLUSTERS, 7, 9
plotMultiEigenvalues, 8
plotTheCluster, 10
temperatureSample, 6, 10
12