---
title: "Social Network Analysis"
author: "Kevin O Brien"
date: "5 December 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(egonet)
```

* Package 'egonet'
* February 19, 2015
* Type Package
* Title Tool for ego-centric measures in Social Network Analysis
* Version 1.2
* Date 2012-11-01
* Author A. Sciandra, F. Gioachin, L. Finos
* Maintainer L. Finos <livio@stat.unipd.it>
* Depends sna

Description A small tool for Social Network Analysis, dealing with
ego-centric network measures, including Burt's effective size
and aggregate constraint and an import code suitable for a
large number of adjacency matrices. A free web application is
also available on http://www.egonet.associazionerospo.org
License GPL (>= 2)
LazyLoad yes
Repository CRAN
Date/Publication 2012-11-11 16:30:56
NeedsCompilation no
R topics documented:
egonet-package . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 2
index.egonet . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 3
read.egonet . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 5


## egonet-package 
Tool for ego-centric measures in Social Network Analysis
Description
A small tool for Social Network Analysis, dealing with ego-centric network measures, including
Burt's effective size and aggregate constraint and an import code suitable for a large number of
adjacency matrices.
The Egonet package is also available as free web application on http://www.egonet.associazionerospo.org
(and an example of output can be seen here: http://www.egonet.associazionerospo.org/egonetdata/EgonetOutput.htm)
Details
Package: egonet
Type: Package
Version: 1.0
Date: 2010-03-11
License: GPL (>= 2)
LazyLoad: yes
Author(s)
A. Sciandra, F. Gioachin, L. Finos
Maintainer: <livio@stat.unipd.it>
References
Burt, R.S. (1992) "Structural Holes. The Social Structure of Competition", Cambridge (MA), Harvard
University Press.
Wasserman, S. and Faust, K. (1994) "Social Network Analysis. Method and Applications", Cambridge
(MA), Cambridge University Press.
See Also
sna
Examples
```{r}
## This is a list of file' names containing the ego-network
ff <- c("q1.csv","q2.csv","q3.csv")
files <- paste("http://www.egonet.associazionerospo.org/egonetdata/",ff,sep="")
names(files) <- ff

##if all your data are in a directory (eg. egonets, containing all files with the same extension),
##you can easily get this list with the following commands
# ff <- dir("./egonets",pattern=".csv")
# files <- paste("./egonets/",ff,sep="")
# names(files) <- ff
# Here is a dataset with demographic informations and the names of files containing the ego-network
#we now want to add network indeces to this data.frame
data <- data.frame( gender=c("F","F","M"), age =(2:4)*10, filename=ff)
data
#import all the egonets
mats <- lapply(files,read.egonet)
#compute (default) indices on the first subject
index.egonet(mats[[1]])
#compute indices on all adjacency matrices
idx <- sapply(mats,index.egonet)
#reshape idx in a data.frame and add the file names
idx <- as.data.frame(t(idx))
idx <- cbind(idx,filename=rownames(idx))
#now merge demographic informations with the indices
data <- merge(data,idx,by="filename")
data
#Compute the \code{effsize} and \code{constraint} to the restricted network with "EGO" and nodes with "P" in the name idx <- sapply(mats,index.egonet, subset = "P",index = c("effsize","constraint"))
rownames(idx) <- paste(rownames(idx),"P",sep=".")
idx <- as.data.frame(t(idx))
idx <- cbind(idx,filename=rownames(idx))
#and merge them to the dataset
data <- merge(data,idx,by="filename")
data
```

index.egonet Compute Burt's indexes (effective size and aggregate constraint) and
other measure from sna package
Description
Compute Burt's indexes (effective size and aggregate constraint) and other measure from sna package.
It also allow to restrict the analysis to one social circle identified by the name of the alters.
4 index.egonet
Usage
index.egonet(dat, index = list("effsize", "constraint", "outdegree", "indegree", "efficiency", "hierarchy", Arguments
dat graph to be analyzed having row and column names in the same order.
index is a list containing prespecified index functions. effsize and constraint
are defined in as in Burt (1992) \ outdegree and indegree make a call of
degree(dat, cmode="outdegree") and degree(dat, cmode="indegree")
and take the element corresponding to ego.name\ ego.gden applies gden in a
matrix without ego.name connections. \ Other indeces are call of the homonimous
functions of package sna. \ If the generic element is.call(index[[h]])
is TRUE, it will be evaluated in the global environment: eval(index[[h]],envir =.GlobalEnv)
(see also example below)
subset Restricts the analysis to the nodes with at least one among the elements of
vector in the name. If vector = NULL - the default - all the nodes of the
graph are comprised.
ego.name column and row name given to the ego subject. The default is EGO
Value
The requested indices.
Author(s)
A. Sciandra, F. Gioachin, L. Finos <livio@stat.unipd.it>
References
Burt, R.S. (1992) "Structural Holes. The Social Structure of Competition", Cambridge (MA), Harvard
University Press.
Examples
```{r}
# make a toy dataset
egomat <- matrix(c(0,1,1,1,0,0,1,0,0),3,3)
colnames(egomat) <- rownames(egomat) <- c("EGO", "1P", "1A")
index.egonet(egomat)
# an example with self defined index
my.outdegree <- function(dat) degree(dat,cmod="outdegree")[1]
index.egonet(egomat,index=c("effsize","constraint","outdegree","indegree","efficiency", "centralization", "gden"))
#Restricts the \code{outdegree} and \code{efficiency} to "EGO" and nodes with "P" in the name
index.egonet(egomat,index=c("outdegree","efficiency"),subset="P")
```


read.egonet Reads ego-centric graph in table format and creates a matrix suitable
for SNA.

#### Description
Reads text table and creates ego-centric graph from it, with the ego actor in the first row and column.
The result is a square matrix with common input/output connection' names.

#### Usage
read.egonet(file, sep=",", dec=".", ego.name="EGO")

#### Arguments
* file the name of the file which the data are to be read from. It must be a square matrix, with node's names in the first row and column. See also file of read.table
* sep as in read.table
* dec as in read.table
* ego.name column and row name given to the ego subject. The default is EGO

#### Value
A square matrix containing the ego-centric network of the data in the file.
Author(s)
F. Gioachin, A. Sciandra, L. Finos <livio@stat.unipd.it>
See Also
read.table
Examples
```{r}
dat <- read.egonet("http://www.egonet.associazionerospo.org/egonetdata/q1.csv")
dat
```