---
title: "afastnet"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(fastnet)
```


Package 'fastnet'
September 11, 2018
Type Package
Title Large-Scale Social Network Analysis
Version 0.1.6
Description We present an implementation of the algorithms required to simulate largescale
social networks and retrieve their most relevant metrics.
License GPL (>= 2)
Imports doParallel (>= 1.0.0), foreach (>= 1.4.0), igraph (>= 1.2.0),
tidygraph(>= 1.1.0)
Depends R (>= 3.5.0)
Encoding UTF-8
LazyData true
BugReports https://github.com/networkgroupR/fastnet/issues
RoxygenNote 6.1.0
NeedsCompilation no
Author Nazrul Shaikh [aut, cre],
Xu Dong [aut],
Luis Castro [aut],
Christian Llano [ctb]
Maintainer Nazrul Shaikh <networkgroupr@gmail.com>
Repository CRAN
Date/Publication 2018-09-11 06:00:02 UTC
R topics documented:
degree.collect . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 3
degree.dist . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 3
degree.hist . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 4
draw.net . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 5
from.adjacency . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 6
from.edgelist . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 7
1
2 R topics documented:
from.igraph . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 7
from.statnet . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 8
metric.cluster.global . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 9
metric.cluster.mean . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 10
metric.cluster.median . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 11
metric.degree.effective . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 12
metric.degree.entropy . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 12
metric.degree.max . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 13
metric.degree.max.efficient . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 14
metric.degree.mean . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 15
metric.degree.median . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 15
metric.degree.min . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 16
metric.degree.sd . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 17
metric.distance.apl . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 18
metric.distance.diameter . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 19
metric.distance.effdia . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 20
metric.distance.meanecc . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 21
metric.distance.medianecc . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 22
metric.distance.mpl . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 23
metric.eigen.mean . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 24
metric.eigen.median . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 25
metric.eigen.value . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 26
metric.graph.density . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 27
neighbors . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 28
net.barabasi.albert . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 28
net.caveman . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 29
net.complete . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 30
net.erdos.renyi.gnm . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 31
net.erdos.renyi.gnp . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 32
net.holme.kim . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 33
net.random.plc . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 34
net.rewired.caveman . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 35
net.ring.lattice . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 36
net.watts.strogatz . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 37
preview.deg . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 38
preview.net . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 38
to.edgelist . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 39
to.igraph . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 40
to.tidygraph . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 40
Index 42
degree.collect 3
degree.collect Degrees of nodes

#### Description
Collect the degrees for all nodes in a network.

#### Usage
<pre><code>

degree.collect(net)

</code></pre>
#### Arguments
net The input network.
Details
Obtain the degrees for all nodes.
#### Value
A vector.
Author(s)
Xu Dong, Nazrul Shaikh.
#### Examples
```{r}
## Not run:
x.deg <- degree.collect(x)
summary(x.deg)
## End(Not run)
degree.dist Plot of the degree distribution of a network

#### Description
Plot the degree distribution of a network.

#### Usage
<pre><code>

degree.dist(net, cumulative = TRUE, log = TRUE)
4 degree.hist

</code></pre>
#### Arguments
net The input network.
cumulative A logical index asking whether a cumulative distribution should be returned.
log A logical index asking whether a logarithm-scaled distribution should be returned.
Details
Plot the degree distribution of a network.
#### Value
A .gif plot.
Author(s)
Xu Dong
#### Examples
```{r}
## Not run:
x <- net.erdos.renyi.gnp(1000, 0.01)
## Plot the standard degree distribution of x.
degree.dist(x, cumulative = FALSE, log = FALSE)
## Plot the degree distribution of x, with a logarithm scale.
degree.dist(x, cumulative = FALSE, log = TRUE)
## Plot the cumulative degree distribution of x.
degree.dist(x, cumulative = TRUE, log = FALSE)
## Plot the cumulative degree distribution of x, with a logarithm scale.
degree.dist(x, cumulative = TRUE, log = TRUE)
## End(Not run)
degree.hist Histogram of the degree distribution of a network

#### Description
Plot the histogram of all degrees of a network.

#### Usage
<pre><code>

degree.hist(g, breaks = 100)
draw.net 5

</code></pre>
#### Arguments
g The input network.
breaks A single number giving the number of cells for the histogram.
Details
Plot the histogram of all degrees of a network.
#### Value
A .gif plot.
Author(s)
Xu Dong
#### Examples
```{r}
## Not run:
x <- net.erdos.renyi.gnp(1000, 0.05)
degree.hist(x)
## End(Not run)
draw.net Plot of a small network

#### Description
Plot a small network.

#### Usage
<pre><code>

draw.net(net)

</code></pre>
#### Arguments
net The input network.
Details
Plot a small network.
#### Value
A .gif plot.
6 from.adjacency
Author(s)
Xu Dong, Nazrul Shaikh.
#### Examples
```{r}
## Not run:
x <- net.ring.lattice(12,4)
draw.net(x)
## End(Not run)
from.adjacency Adjacency Matrix to fastnet

#### Description
Transform an adjacency matrix to an ego-centric list form used in fastnet.

#### Usage
<pre><code>

from.adjacency(adj.mat)

</code></pre>
#### Arguments
adj.mat The input adjacency matrix
#### Value
A list containing the nodes of the network and their respective neighbors.
Author(s)
Xu Dong, Christian Llano.
#### Examples
```{r}
adj.mat <- matrix(c(0,1,0,0,1,0,0,0,0,0,0,1,0,0,1,0), nrow = 4, ncol = 4)
g <- from.adjacency(adj.mat)
from.edgelist 7
from.edgelist Edgelist to fastnet

#### Description
Transform an edgelist to an ego-centric list form used in fastnet.

#### Usage
<pre><code>

from.edgelist(edgelist)

</code></pre>
#### Arguments
edgelist A 2-column data frame, in which the 1st column represents the start nodes, and
the 2nd column represents the destination nodes.
Details
Most network data repositories choose to store the data in an edgelist form. This function helps user
to load it in fastnet.
#### Value
A list containing the nodes of the network and their respective neighbors.
Author(s)
Xu Dong
#### Examples
```{r}
edgelist <- data.frame(from=c(1, 3, 2, 3, 3), to=c(4, 5, 6, 5, 7))
g <- from.edgelist(edgelist)
from.igraph Transform an igraph object to a fastnet object

#### Description
Transform an igraph object to an ego-centric list form used in fastnet.

#### Usage
<pre><code>

from.igraph(net.igraph)
8 from.statnet

</code></pre>
#### Arguments
net.igraph The input igraph object.
#### Value
A list containing the nodes of the network and their respective neighbors.
Author(s)
Xu Dong.
#### Examples
```{r}
## Not run:
library("igraph")
net.igraph <- erdos.renyi.game(100,0.1)
g <- from.igraph(net.igraph)
## End(Not run)
from.statnet statnet to fastnet

#### Description
Import a statnet object.

#### Usage
<pre><code>

from.statnet(net.statnet, ncores = detectCores())

</code></pre>
#### Arguments
net.statnet The input statnet object.
ncores The number of cores to be used.
#### Value
A list containing the nodes of the network and their respective neighbors.
Author(s)
Xu Dong
metric.cluster.global 9
#### Examples
```{r}
## Not run:
library("ergm")
library("doParallel")
data("flo")
nflo <- network(flo, loops = TRUE)
fflo <- from.statnet(nflo)
## End(Not run)
metric.cluster.global Global Clustering Coefficient

#### Description
Calculate the global clustering coefficient of a graph.

#### Usage
<pre><code>

metric.cluster.global(g)

</code></pre>
#### Arguments
g The input network.
Details
The global clustering coefficient measures the ratio of (closed) triples versus the total number of all
possible triples in network g. metric.cluster.global() calculates the global clustering coefficient
of g.
#### Value
A real constant.
Author(s)
Xu Dong, Nazrul Shaikh.
References
Wasserman, Stanley, and Katherine Faust. Social network analysis: Methods and applications. Vol.
8. Cambridge university press, 1994.
#### Examples
```{r}
## Not run:
x <- net.erdos.renyi.gnp(1000, 0.01)
metric.cluster.global(x)
## End(Not run)
10 metric.cluster.mean
metric.cluster.mean Mean Local Clustering Coefficient

#### Description
Calculate the average local clustering coefficient of a graph.

#### Usage
<pre><code>

metric.cluster.mean(g)

</code></pre>
#### Arguments
g The input network.
Details
The local clustering coefficient of a node is the ratio of the triangles connected to the node and the
triples centered on the node.metric.cluster.mean() calculates the (estimated) average clustering
coefficient for all nodes in graph g with a justified error.
#### Value
A real constant.
Author(s)
Xu Dong, Nazrul Shaikh.
References
Wasserman, Stanley, and Katherine Faust. Social network analysis: Methods and applications. Vol.
8. Cambridge university press, 1994.
#### Examples
```{r}
## Not run:
x <- net.erdos.renyi.gnp(n = 1000, ncores = 3, p = 0.06)
metric.cluster.mean(x)
## End(Not run)
metric.cluster.median 11
metric.cluster.median Median Local Clustering Coefficient

#### Description
Calculate the median local clustering coefficient of a graph.

#### Usage
<pre><code>

metric.cluster.median(g)

</code></pre>
#### Arguments
g The input network.
Details
The local clustering coefficient of a node is the ratio of the triangles connected to the node and
the triples centered on the node.metric.cluster.median() calculates the (estimated) median
clustering coefficient for all nodes in graph g with a justified error.
#### Value
A real constant.
Author(s)
Xu Dong, Nazrul Shaikh.
References
Wasserman, Stanley, and Katherine Faust. Social network analysis: Methods and applications. Vol.
8. Cambridge university press, 1994.
#### Examples
```{r}
## Not run:
x <- net.erdos.renyi.gnp(1000, 0.1)
metric.cluster.median(x)
## End(Not run)
12 metric.degree.entropy
metric.degree.effective
Effective Degree

#### Description
Calculate the effective degree of a network.

#### Usage
<pre><code>

metric.degree.effective(g, effective_rate = 0.9)

</code></pre>
#### Arguments
g The input network.
effective_rate The effective rate (0.9 is set by default).
Details
The effective degree
#### Value
A real constant.
Author(s)
Xu Dong, Nazrul Shaikh.
#### Examples
```{r}
## Not run:
metric.degree.effective(x)
## End(Not run)
metric.degree.entropy Degree Entropy

#### Description
Calculate the degree entropy of a graph.

#### Usage
<pre><code>

metric.degree.entropy(g)
metric.degree.max 13

</code></pre>
#### Arguments
g The input network.
Details
Calculates the degree entropy of graph g, i.e.
Entropy(g) = ????
Xn
i=1
i  log2(i)
#### Value
A real constant.
Author(s)
Xu Dong, Nazrul Shaikh.
References
Anand, Kartik, and Ginestra Bianconi. "Entropy measures for networks: Toward an information
theory of complex topologies." Physical Review E 80, no. 4 (2009): 045102.
#### Examples
```{r}
## Not run:
x <- net.erdos.renyi.gnp(1000, 0.01)
metric.degree.entropy(x)
## End(Not run)
```

metric.degree.max Maximal Degree

#### Description
Calculate the maximal degree of a graph.

#### Usage
<pre><code>

metric.degree.max(g)

</code></pre>
#### Arguments
g The input network.
Details
The maximal degree.

#### Value
A real constant.
Author(s)
Xu Dong, Nazrul Shaikh.
#### Examples
```{r}
## Not run:
metric.degree.max(x)
## End(Not run)
metric.degree.max.efficient
Efficient Maximal Degree

#### Description
Calculate the efficient maximal degree of a graph.

#### Usage
<pre><code>

metric.degree.max.efficient(g)

</code></pre>
#### Arguments
g The input network.
Details
The efficient maximal degree is the 90
#### Value
A real constant.
Author(s)
Xu Dong, Nazrul Shaikh.
#### Examples
```{r}
## Not run: x <- net.erdos.renyi.gnp(1000, 0.01)
metric.degree.max.efficient(x)
## End(Not run)
metric.degree.mean 15
metric.degree.mean Mean Degree

#### Description
Calculate the mean degree of a graph.

#### Usage
<pre><code>

metric.degree.mean(g)

</code></pre>
#### Arguments
g The input network.
Details
The mean degree is the average value of the degrees of all nodes in graph g.
#### Value
A real constant.
Author(s)
Xu Dong, Nazrul Shaikh.
#### Examples
```{r}
## Not run:
x <- net.erdos.renyi.gnp(1000, 0.01)
metric.degree.mean(x)
## End(Not run)
metric.degree.median Median Degree

#### Description
Calculate the median degree of a graph.

#### Usage
<pre><code>

metric.degree.median(g)
16 metric.degree.min

</code></pre>
#### Arguments
g The input network.
Details
The median degree is the median value of the degrees of all nodes in graph g.
#### Value
A real constant.
Author(s)
Xu Dong, Nazrul Shaikh.
#### Examples
```{r}
## Not run:
x <- net.erdos.renyi.gnp(1000, 0.01)
metric.degree.median(x)
## End(Not run)
metric.degree.min Minimal Degree

#### Description
Calculate the minimal degree of a network.

#### Usage
<pre><code>

metric.degree.min(g)

</code></pre>
#### Arguments
g The input network.
Details
The minimal degree.
#### Value
A real constant.
Author(s)
Xu Dong, Nazrul Shaikh.
metric.degree.sd 17
#### Examples
```{r}
## Not run:
metric.degree.min(x)
## End(Not run)
metric.degree.sd Standard Deviation of Degree Distribution

#### Description
Calculate the standard deviation of all degrees of a network.

#### Usage
<pre><code>

metric.degree.sd(g)

</code></pre>
#### Arguments
g The input network.
Details
The standard deviation of all degrees of a network.
#### Value
A real constant.
Author(s)
Xu Dong, Nazrul Shaikh.
#### Examples
```{r}
## Not run:
metric.degree.sd(x)
## End(Not run)
18 metric.distance.apl
metric.distance.apl Average Path Length

#### Description
Calculate the average path length of a graph.

#### Usage
<pre><code>

metric.distance.apl(Network, probability = 0.95, error = 0.03,
Cores = detectCores(), full.apl = FALSE)

</code></pre>
#### Arguments
Network The input network.
probability The confidence level probability.
error The sampling error.
Cores Number of cores to use in the computations. By default uses parallel function
detecCores().
full.apl It will calculate the sampling version by default. If it is set to true, the population
APL will be calculated and the rest of the parameters will be ignored.
Details
The average path length (APL) is the average shortest path lengths of all pairs of nodes in graph
Network. metric.distance.apl calculates the population APL and estimated APL of graph g
with a sampling error set by the user.
The calculation uses a parallel load balancing approach, distributing jobs equally among the cores
defined by the user.
#### Value
A real value.
Author(s)
Luis Castro, Nazrul Shaikh.
References
E. W. Dijkstra. 1959. A note on two problems in connexion with graphs. Numer. Math. 1, 1
(December 1959), 269-271.
Castro L, Shaikh N. Estimation of Average Path Lengths of Social Networks via Random Node Pair
Sampling. Department of Industrial Engineering, University of Miami. 2016.
metric.distance.diameter 19
#### Examples
```{r}
## Not run:
##Default function
x <- net.erdos.renyi.gnp(1000,0.01)
metric.distance.apl(x)
##Population APL
metric.distance.apl(x, full.apl=TRUE)
##Sampling at 99% level with an error of 10% using 5 cores
metric.distance.apl(Network = x, probability=0.99, error=0.1, Cores=5)
## End(Not run)
metric.distance.diameter
Diameter

#### Description
Calculate the diameter of a graph.

#### Usage
<pre><code>

metric.distance.diameter(Network, probability = 0.95, error = 0.03,
Cores = detectCores(), full = TRUE)

</code></pre>
#### Arguments
Network The input network.
probability The confidence level probability
error The sampling error
Cores Number of cores to use in the computations. By default uses parallel function
detecCores().
full It will calculate the popular full version by default. If it is set to FALSE, the
estimated diameter will be calculated.
Details
The diameter is the largest shortest path lengths of all pairs of nodes in graph Network.
metric.distance.diameter calculates the (estimated) diameter of graph Network with a justified
error.
#### Value
A real value.
20 metric.distance.effdia
Author(s)
Luis Castro, Nazrul Shaikh.
References
E. W. Dijkstra. 1959. A note on two problems in connexion with graphs. Numer. Math. 1, 1
(December 1959), 269-271.
Castro L, Shaikh N. Estimation of Average Path Lengths of Social Networks via Random Node Pair
Sampling. Department of Industrial Engineering, University of Miami. 2016.
#### Examples
```{r}
## Not run:
##Default function
x <- net.erdos.renyi.gnp(1000,0.01)
metric.distance.diameter(x)
##Population APL
metric.distance.diameter(x, full=TRUE)
##Sampling at 99% level with an error of 10% using 5 cores
metric.distance.diameter(Network = x, probability=0.99, error=0.1, Cores=5)
## End(Not run)
metric.distance.effdia
Effective Diameter

#### Description
Calculate the effective diameter of a graph.

#### Usage
<pre><code>

metric.distance.effdia(Network, probability = 0.95, error = 0.03,
effective_rate = 0.9, Cores = detectCores(), full = TRUE)

</code></pre>
#### Arguments
* network The input network.
* probability The confidence level probability
* error The sampling error
* effective_rate The effective rate (by default it is set to be 0.9)
* Cores Number of cores to use in the computations. By default uses parallel function detecCores().
* full It will calculate the popular full version by default. If it is set to FALSE, the estimated diameter will be calculated.

#### Details
The diameter is the largest shortest path lengths of all pairs of nodes in graph Network.

metric.distance.diameter
calculates the (estimated) diameter of graph Network with a justified error.
#### Value
A real value.
Author(s)
Luis Castro, Nazrul Shaikh.
References
DijkstraEW. A note on two problems in connexion with graphs:(numerische mathematik, _1 (1959),
p 269-271). 1959.
Castro L, Shaikh N. Estimation of Average Path Lengths of Social Networks via Random Node Pair
Sampling. Department of Industrial Engineering, University of Miami. 2016.
#### Examples
```{r}
## Not run:
##Default function
x <- net.erdos.renyi.gnp(1000,0.01)
metric.distance.effdia(x)
##Population APL
metric.distance.effdia(x, full=TRUE)
##Sampling at 99% level with an error of 10% using 5 cores
metric.distance.effdia(Network = x, probability=0.99, error=0.1, Cores=5)
## End(Not run)
```

metric.distance.meanecc Mean Eccentricity

#### Description
Calculate the mean eccentricity of a graph.

#### Usage
<pre><code>

metric.distance.meanecc(g, p)

</code></pre>
#### Arguments
* ``g``: The input network.
* ``p``: The sampling probability.

#### Details
The mean eccentricities of all nodes in graph g. Calculates the (estimated) mean eccentricity of
graph g with a justified error.
#### Value
A real constant.
Author(s)
Xu Dong, Nazrul Shaikh.
References
West, Douglas Brent. Introduction to graph theory. Vol. 2. Upper Saddle River: Prentice Hall,
2001.
#### Examples
```{r}
## Not run:
x <- net.erdos.renyi.gnp(1000, 0.01)
metric.distance.meanecc(x, 0.01)
## End(Not run)
metric.distance.medianecc
Median Eccentricity

#### Description
Calculate the (estimated) median eccentricity of a graph.

#### Usage
<pre><code>

metric.distance.medianecc(g, p)

</code></pre>
#### Arguments
* g The input network.
* p The sampling probability.

#### Details
Is the median eccentricities of all nodes in graph g. metric.distance.medianecc calculates the (estimated) median eccentricity of graph g with a justified error.

#### Value
A real constant.
Author(s)
Xu Dong, Nazrul Shaikh.
References
West, Douglas Brent. Introduction to graph theory. Vol. 2. Upper Saddle River: Prentice hall, 2001.
#### Examples
```{r}
## Not run:
x <- net.erdos.renyi.gnp(1000, 0.01)
metric.distance.medianecc(x, 0.01)
## End(Not run)
metric.distance.mpl Median Path Length

#### Description
Calculate the median path length (MPL) of a network.

#### Usage
<pre><code>

metric.distance.mpl(Network, probability = 0.95, error = 0.03,
Cores = detectCores(), full = FALSE)

</code></pre>
#### Arguments
* Network The input network.
* probability The confidence level probability
* error The sampling error
* Cores Number of cores to use in the computations. By default detecCores() from
parallel.
* full It calculates the sampling version by default. If it is set to true, the population
MPL will be calculated and the rest of the parameters will be ignored.

#### Details
The median path length (MPL) is the median shortest path lengths of all pairs of nodes in Network.
metric.distance.mpl(g) calculates the population MPL OR estimated MPL of network g with a sampling
error set by the user. The calculation uses a parallel load balancing approach, distributing jobs

#### Value
A real integer
Author(s)
Luis Castro, Nazrul Shaikh.
References
E. W. Dijkstra. 1959. A note on two problems in connexion with graphs. Numer. Math. 1, 1
(December 1959), 269-271.
Castro L, Shaikh N. Estimation of Average Path Lengths of Social Networks via Random Node Pair
Sampling. Department of Industrial Engineering, University of Miami. 2016.
#### Examples
```{r}
## Not run:
##Default function
x <- net.erdos.renyi.gnp(1000,0.01)
metric.distance.mpl(x)
##Population MPL
metric.distance.mpl(x, full=TRUE)
##Sampling at 99% level with an error of 10% using 5 cores
metric.distance.mpl(Network = x, probability=0.99, error=0.1, Cores=5)
## End(Not run)
metric.eigen.mean Mean Eigenvalue Centrality

#### Description
Calculate the mean eigenvalue centrality of a graph.

#### Usage
<pre><code>

metric.eigen.mean(g)

</code></pre>
#### Arguments
g The input network.
Details
metric.eigen.mean calculates the mean eigenvalue centrality score of graph g.
metric.eigen.median 25
#### Value
A real constant.
Author(s)
Xu Dong, Nazrul Shaikh.
References
Bonacich, Phillip, and Paulette Lloyd. "Eigenvector-like measures of centrality for asymmetric
relations." Social networks 23, no. 3 (2001): 191-201.
Borgatti, Stephen P. "Centrality and network flow." Social networks 27, no. 1 (2005): 55-71.
#### Examples
```{r}
## Not run:
x <- net.erdos.renyi.gnp(1000, 0.01)
metric.eigen.mean(x)
## End(Not run)
metric.eigen.median Median Eigenvalue Centrality

#### Description
Calculate the median eigenvalue centrality of a graph.

#### Usage
<pre><code>

metric.eigen.median(g)

</code></pre>
#### Arguments
g The input network.
Details
metric.eigen.median calculates the median eigenvalue centrality score of graph g.
#### Value
A real constant.
Author(s)
Xu Dong, Nazrul Shaikh.
26 metric.eigen.#### Value
References
Bonacich, Phillip, and Paulette Lloyd. "Eigenvector-like measures of centrality for asymmetric
relations." Social networks 23, no. 3 (2001): 191-201.
Borgatti, Stephen P. "Centrality and network flow." Social networks 27, no. 1 (2005): 55-71.
#### Examples
```{r}
## Not run:
x <- net.erdos.renyi.gnp(1000, 0.01)
metric.eigen.median(x)
## End(Not run)
metric.eigen.value Eigenvalue Score

#### Description
Calculate the eigenvalue centrality score of a graph.

#### Usage
<pre><code>

metric.eigen.value(g)

</code></pre>
#### Arguments
g The input network.
Details
metric.eigen.value calculates the eigenvalue centrality score of graph g.
#### Value
A real constant.
Author(s)
Xu Dong, Nazrul Shaikh.
References
Bonacich, Phillip, and Paulette Lloyd. "Eigenvector-like measures of centrality for asymmetric
relations." Social networks 23, no. 3 (2001): 191-201.
Borgatti, Stephen P. "Centrality and network flow." Social networks 27, no. 1 (2005): 55-71.
metric.graph.density 27
#### Examples
```{r}
## Not run:
x <- net.erdos.renyi.gnp(1000, 0.01)
metric.eigen.value(x)
## End(Not run)
metric.graph.density Graph Density

#### Description
Calculate the density of a graph.

#### Usage
<pre><code>

metric.graph.density(g)

</code></pre>
#### Arguments
g The input network.
Details
Computes the ratio of the number of edges and the number of possible edges.
#### Value
A real constant.
Author(s)
Xu Dong, Nazrul Shaikh.
#### Examples
```{r}
## Not run:
x <- net.erdos.renyi.gnp(1000, 0.01)
metric.graph.density(x)
## End(Not run)
28 net.barabasi.albert
neighbors Neighbors of an agent in a network

#### Description
Presents all neighbors of a given node.

#### Usage
<pre><code>

neighbors(net, NodeID)

</code></pre>
#### Arguments
net The input network.
NodeID The ID of the input node.
Details
Neighbors of a node are nodes that directly connects to this node.
#### Value
A vector.
Author(s)
Xu Dong
#### Examples
```{r}
## Not run:
x <- net.ring.lattice(12,4)
neighbors(x,2)
## End(Not run)
net.barabasi.albert Barabasi-Albert Scale-free Graph

#### Description
Simulate a scale-free network using a preferential attachment mechanism (Barabasi and Albert,
1999)

#### Usage
<pre><code>

net.barabasi.albert(n, m, ncores = detectCores(), d = FALSE)
net.caveman 29

</code></pre>
#### Arguments
n Number of nodes of the network.
m Number of nodes to which a new node connects at each iteration.
ncores Number of cores, by default detectCores() from parallel.
d A logical value determining whether the generated network is a directed or undirected
(default) network.
Details
Starting with m nodes, the preferential attachment mechaism adds one node and m edges in each
step. The edges will be placed with one end on the newly-added node and the other end on the
existing nodes, according to probabilities that associate with their current degrees.
#### Value
A list containing the nodes of the network and their respective neighbors.
Author(s)
Luis Castro, Xu Dong, Nazrul Shaikh.
References
Barabasi, A.- L. and Albert R. 1999. Emergence of scaling in random networks. Science, 286
509-512.
#### Examples
```{r}
## Not run:
x <- net.barabasi.albert(1000, 20) # using default ncores
## End(Not run)
net.caveman Caveman Network

#### Description
Simulate a (connected) caveman network of m cliques of size k.

#### Usage
<pre><code>

net.caveman(m, k, ncores = detectCores())

</code></pre>
#### Arguments
m Number of cliques (or caves) in the network.
k Number of nodes per clique.
ncores Number of cores, by default detectCores() from parallel.
30 net.complete
Details
The (connected) caveman network is formed by connecting a set of isolated k - cliques (or "caves"),
neighbor by neighbor and head to toe, using one edge that removed from each clique such that all
m cliques form a single circle (Watts 1999). The total number of nodes, i.e. n, in this network is
given by k  m.
#### Value
A list containing the nodes of the network and their respective neighbors.
Author(s)
Xu Dong, Nazrul Shaikh.
References
Watts, D. J. Networks, Dynamics, and the Small-World Phenomenon. Amer. J. Soc. 105, 493-527,
1999.
#### Examples
```{r}
## Not run:
x <- net.caveman(50, 20) #using ncores by default
## End(Not run)
net.complete Complete Network

#### Description
Simulate a complete (or full) network.

#### Usage
<pre><code>

net.complete(n, ncores = detectCores())

</code></pre>
#### Arguments
n Number of nodes of the network.
ncores Number of cores, by default detectCores() from parallel.

#### Details
The n nodes in the network are fully connected.
Note that the input n should not excess 10000, for the sake of memory overflow.
net.erdos.renyi.gnm 31
#### Value
A list containing the nodes of the network and their respective neighbors.
Author(s)
Xu Dong, Nazrul Shaikh.
#### Examples
```{r}
## Not run:
x <- net.complete(1000) #using ncores by default
## End(Not run)
net.erdos.renyi.gnm Directed / Undirected Erdos-Renyi G(n;m) network using a fix edge
size.

#### Description
Simulate a random network with n nodes and m edges, according to Erdos and Renyi (1959).

#### Usage
<pre><code>

net.erdos.renyi.gnm(n, m, ncores = detectCores(), d = TRUE)

</code></pre>
#### Arguments
n Number of nodes of the network.
m Number of edges of the network.
ncores Number of cores, by default detectCores() from parallel.
d A logical value determining whether is a network directed (default) or indirected.
Details
In this (simplest) random network, m edges are formed at random among n nodes. When d = TRUE
is a directed network.
#### Value
A list containing the nodes of the network and their respective neighbors.
Author(s)
Xu Dong, Nazrul Shaikh.
32 net.erdos.renyi.gnp
References
Erdos, P. and Renyi, A., On random graphs, Publicationes Mathematicae 6, 290-297 (1959).
#### Examples
```{r}
## Not run:
x <- net.erdos.renyi.gnm(1000, 100)
## End(Not run)
net.erdos.renyi.gnp Directed / Undirected Erdos-Renyi G(n; p) network

#### Description
Simulate a random network with n nodes and a link connecting probability of p, according to Edos
and Renyi (1959).

#### Usage
<pre><code>

net.erdos.renyi.gnp(n, p, ncores = detectCores(), d = TRUE)

</code></pre>
#### Arguments
n Number of nodes of the network.
p Connecting probability.
ncores Number of cores, by default detectCores() from parallel.
d A logical value determining whether is a network directed (default) or indirected.
Details
In this (simplest) random network, each edge is formed at random with a constant probability. When
d = TRUE is a directed network.
#### Value
A list containing the nodes of the network and their respective neighbors.
Author(s)
Luis Castro, Xu Dong, Nazrul Shaikh.
References
Erdos, P. and Renyi, A., On random graphs, Publicationes Mathematicae 6, 290-297 (1959).
net.holme.kim 33
#### Examples
```{r}
## Not run:
x <- net.erdos.renyi.gnp(1000, 0.01)
## End(Not run)
net.holme.kim Holme-Kim Network

#### Description
Simulate a scale-free network with relatively high clustering, comparing to B-A networks (Holme
and Kim, 1999).

#### Usage
<pre><code>

net.holme.kim(n, m, pt)

</code></pre>
#### Arguments
n Number of nodes of the network.
m Number of nodes to which a new node connects at each iteration.
pt Triad formation probability after each preferential attachment mechanism.
Details
The Holme-Kim network model is a simple extension of B-A model. It adds an additional step,
called "Triad formation", with the probability pt that compensates the low clustering in B-A networks.
#### Value
A list containing the nodes of the network and their respective neighbors.
Author(s)
Xu Dong, Nazrul Shaikh
References
Holme, Petter, and Beom Jun Kim. "Growing scale-free networks with tunable clustering."Physical
review E65, no. 2 (2002): 026107.
#### Examples
```{r}
## Not run:
x <- net.holme.kim (1000, 20, 0.1)
## End(Not run)
34 net.random.plc
net.random.plc Random Network with a Power-law Degree Distribution that Has An
Exponential Cutoff

#### Description
Simulate a random network with a power-law degree distribution that has an exponential cutoff,
according to Newman et al. (2001).

#### Usage
<pre><code>

net.random.plc(n, cutoff, exponent)

</code></pre>
#### Arguments
n The number of the nodes in the network.
cutoff Exponential cutoff of the degree distribution of the network.
exponent Exponent of the degree distribution of the network.
Details
The generated random network has a power-law degree distribution with an exponential degree
cutoff.
#### Value
A list containing the nodes of the network and their respective neighbors.
Author(s)
Xu Dong, Nazrul Shaikh
References
Newman, Mark EJ, Steven H. Strogatz, and Duncan J.Watts. "Random graphs with arbitrary degree
distributions and their applications." Physical review E 64, no. 2 (2001): 026118.
#### Examples
```{r}
## Not run:
x <- net.random.plc(1000, 10, 2)
## End(Not run)
net.rewired.caveman 35
net.rewired.caveman Rewired (Connected) Caveman Network

#### Description
Simulate a rewired caveman network of m cliques of size k, and with a link rewiring probability p.

#### Usage
<pre><code>

net.rewired.caveman(nc, m, p)

</code></pre>
#### Arguments
nc Number of cliques (or caves) in the network.
m Number of nodes per clique.
p Link rewiring probability.
Details
The rewired caveman network is built on the corresponding regular caveman network with m cliques
of size k. Then the links in this caveman network are rewired with probability p.
#### Value
A list containing the nodes of the network and their respective neighbors.
Author(s)
Xu Dong, Nazrul Shaikh
References
Watts, D. J. Networks, Dynamics, and the Small-World Phenomenon. Amer. J. Soc. 105, 493-527,
1999.
#### Examples
```{r}
## Not run:
x <- net.rewired.caveman(50, 20, 0.0005)
## End(Not run)
36 net.ring.lattice
net.ring.lattice k - regular ring lattice

#### Description
Simulate a network with a k -regular ring lattice structure.

#### Usage
<pre><code>

net.ring.lattice(n, k)

</code></pre>
#### Arguments
n Number of nodes in the network.
k Number of edges per node.
Details
The n nodes are placed on a circle and each node is connected to the nearest k neighbors.
#### Value
A list containing the nodes of the network and their respective neighbors.
Author(s)
Xu Dong, Nazrul Shaikh
References
Duncan JWatts and Steven H Strogatz: Collective dynamics of 'small world' networks, Nature 393,
440-442, 1998.
#### Examples
```{r}
## Not run:
x <- net.ring.lattice(1000, 10)
## End(Not run)
net.watts.strogatz 37
net.watts.strogatz Watts-Strogatz Small-world Network

#### Description
Simulate a small-world network according to the model of Watts and Strogatz (1998).

#### Usage
<pre><code>

net.watts.strogatz(n, k, re)

</code></pre>
#### Arguments
n The number of the nodes in the network (or lattice).
k Number of edges per node.
re Rewiring probability.
Details
The formation of Watts-Strogatz network starts with a ring lattice with n nodes and k edges per
node, then each edge is rewired at random with probability re.
#### Value
A list containing the nodes of the network and their respective neighbors.
Author(s)
Xu Dong, Nazrul Shaikh
References
Duncan J. Watts and Steven H. Strogatz: Collective dynamics of 'small world' networks, Nature
393, 440-442, 1998.
#### Examples
```{r}
## Not run:
x <- net.watts.strogatz(1000, 10, 0.05)
## End(Not run)
38 preview.net
preview.deg Preview of the degree distribution of a network

#### Description
Present the first 10 degrees of a network.

#### Usage
<pre><code>

preview.deg(g)

</code></pre>
#### Arguments
g The input network.
Details
Present the first 10 degrees of a network.
#### Value
A vector.
Author(s)
Xu Dong, Nazrul Shaikh.
#### Examples
```{r}
## Not run:
x <- net.ring.lattice(12,4)
preview.deg(x)
## End(Not run)
preview.net Preview of a network

#### Description
Present the first 10 ego-centric lists of a network.

#### Usage
<pre><code>

preview.net(net)
to.edgelist 39

</code></pre>
#### Arguments
net The input network.
Details
the connection condition of the first 10 nodes in a network.
#### Value
A list.
Author(s)
Xu Dong, Nazrul Shaikh.
#### Examples
```{r}
## Not run:
x <- net.ring.lattice(12,4)
preview.net(x)
## End(Not run)
to.edgelist fastnet to edgelist

#### Description
Coerce a fastnet object to edgelist.

#### Usage
<pre><code>

to.edgelist(network, ncores)

</code></pre>
#### Arguments
network A fastnet object.
ncores The number of cores to be used.
#### Value
A 2-column list with each row representing an edge, from source to destination
Author(s)
Xu Dong
40 to.tidygraph
#### Examples
```{r}
## Not run:
g <- net.erdos.renyi.gnp(100, 0.1)
el <- to.edgelist(g)
## End(Not run)
to.igraph fastnet to igraph

#### Description
Coerce a fastnet object to an igraph object

#### Usage
<pre><code>

to.igraph(g)

</code></pre>
#### Arguments
g A fastnet object
#### Value
An igraph object
Author(s)
Xu Dong
to.tidygraph fastnet to tidygraph

#### Description
Coerce a fastnet object to a tidygraph object.

#### Usage
<pre><code>

to.tidygraph(g)

</code></pre>
#### Arguments
g A fastnet object.
#### Value
A tidygraph object
to.tidygraph 41
Author(s)
Xu Dong
