---
title: "``bigdatadist::entropy.fd``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(bigdatadist)
```

Functional Entropy Measures

#### Description 
This function allows you to compute the family of alpha-Entropy for functional data as stated in Martos et al (2018).

#### Usage

<pre><code>
entropy.fd(fdframe, gamma = 1, kerfunc="rbf",
kerpar = list(sigma = 1, bias=0,degree=2),
alpha=2,d=2,resol,k.neighbor)
</code></pre>

#### Arguments 
* ``fdframe``: functional data frame fdframe object.
* ``gamma``: regularization parameter.
* ``kerfunc``: kernel function (``rbf`` or ``poly``) to be used.
* ``kerpar``: a list of kernel parameters where sigma is the scale with both kernels.
* ``alpha``: Entropy parameter.
* ``d``: Dimension truncation in the Reproducing Kernel Hilbert Space representation.
* ``resol``: number of level sets used to compute the functional entropy.
* ``k.neighbor``: number of points to estimate the support of the distribution.

#### Examples 

```{r}
data(Ausmale); t <- Ausmale[[1]]
t <- as.numeric(( t - min(t) ) / length(t))
raw.data <- fdframe(t=t, Y=Ausmale[[2]])
entropy.fd(raw.data,gamma=0.0001,kerfunc="rbf",kerpar=c(10),
alpha=2, k.neighbor=15)
```

#### Details
This function estimates the entropy of a stochastic process. To this aim, the raw functional data is projected onto a Reproducing Kernel Hilbert Space, and the entropy is estimated using the coefficient of these functions.

#### Value
* ``local.entropy``: local entropy relative to each curve in the sample.
* ``entropy``: estimated entropy of the the set of functions.

#### Author(s)
Hernandez and Martos

#### References
Martos, G. et al (2018). Entropy Measures for Stochastic Processes with Applications in Functional Anomaly Detection. Entropy 20(1), 33 (2018).
