---
title: "``bigdatadist::rkhs``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(bigdatadist)
```
## RKHS Representation

#### Description 

This function allows you to fit discrete functional data (fdframe) as functions in RKHS solving a regularization problem as stated in Munoz (2010).

#### Usage

<pre><code>
rkhs(fdframe, gamma=1, kerfunc='rbf',
kerpar=list(sigma=1, bias=0, degree=2))
</code></pre>

#### Arguments 

* ``fdframe``: functional data fdframe object.
* ``gamma``: regularization parameter.
* ``kerfunc``: kernel function rbf or poly to be used.
* ``kerpar``: a list of kernel parameters where sigma is the scale with both kernels.

#### Examples 

```{r}
data(merval); t <- as.Date(merval[1:100,1])
t <- as.numeric(( t - min(t) ) / 154)
raw.data <-fdframe(t = t, Y = merval[1:100,2:5])
plot(raw.data, xlab='time', ylab='Merval raw data')
f.data <- rkhs(raw.data, gamma = 0.001, kerpar = list(sigma = 8))
print(f.data)
plot(f.data, xlab='time', ylab='Merval data')
```

#### Value

* ``fdframe``: raw data in an fdframe object.
* ``f``: estimated functional data
* ``alpha``: coefficients for the linear combination.
* ``lambda.star``: reduced coefficients for the linear combination.

#### Author(s)
Hernandez and Martos

#### References
Munoz A. et al (2010). Representing functional data using support vector machines. Pattern recog-
nition letters, 31(6).
