---
title: "``DataVisualizations::``"
output: html_document
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(DataVisualizations)
```
ClassMDplot Class MD-plot for Data w.r.t. all classes

#### Description
Creates PDE optimized Violin plot for all classes

#### Usage

<pre><code>
ClassMDplot(Data, Cls, ColorSequence,
  ClassNames = NULL,
  PlotLegend = TRUE,
  main = 'PDE Violin Plot for each Class',
  xlab = 'Classes',
  ylab = 'PDE of Data per Class',MinimalAmoutOfData=40)
</code></pre>

#### Arguments
* Data [1:n] Vector of the data to be plotted
* Cls [1:n] Vector of class identifiers of k clusters one number is the label of one
cluster
* ColorSequence Optional: [1:k] vector, The sequence of colors used, Default: DataVisualizations::
DefaultColorSequence
ClassNames Optional: [1:k] vector, The names of the classes. Default: C1 - C(Number of Classes)
* PlotLegend Optional: Add a legent to plot. Default: TRUE)
* main Optional: Title of the plot. Default: "ClassViolinPlot""
* xlab Optional: Title of the x axis. Default: "Classes"
* ylab Optional: Title of the y axis. Default: "Data"
MinimalAmoutOfData
Optional: numeric value defining a threshold. Below this threshold no density
estimation is performed and a Jitter plot with a median line is drawn. Please see
MDplot for details.

#### Details
The Cls vector is sorted from lowest to highest number. The ClassNames vector and ColorSequence
vectors are matched by this ordering of Cls, i.e. the lowest number gets the first color or class name.

#### Value
A List of
ClassData The DataFrame used to plot
ggobject The ggplot2 plot object
in mode invisible


#### Examples
```{r}
data(ITS)
model=AdaptGauss::AdaptGauss(ITS)
Classification=AdaptGauss::ClassifyByDecisionBoundaries(ITS,
DecisionBoundaries = AdaptGauss::BayesDecisionBoundaries(model$Means,model$SDs,model$Weights))
DataVisualizations::ClassMDplot(ITS,Classification)
```

#### Author(s)
Michael Thrun, Felix Pape

#### References
Thrun, M. C., Pape, F., & Ultsch, A. : Benchmarking Cluster Analysis Methods using PDEOptimized
Violin Plots, Proc. European Conference on Data Analysis (ECDA), accepted, Paderborn,
Germany, 2018.
Thrun, M. C., Breuer, L., & Ultsch, A. : Knowledge discovery from low-frequency stream nitrate
concentrations: hydrology and biology contributions, Proc. European Conference on Data Analysis
(ECDA), accepted, Paderborn, Germany, 2018.
14 ClassPDEplot
