---
title: "``DataVisualizations::ClassBoxplot``"
output: html_document
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(DataVisualizations)
```

ClassBoxplot Creates Boxplot plot for all classes
#### Description
Boxplot the data for all classes
#### Usage
<pre><code>
ClassBoxplot(Data, Cls, ColorSequence = DataVisualizations::DefaultColorSequence,
ClassNames = NULL, PlotLegend = TRUE,
main = 'Boxplot per Class', xlab = 'Classes', ylab = 'Range of Data')
</code></pre>

#### Arguments

* Data Vector of the data to be plotted
* Cls Vector of class identifiers.
* ColorSequence Optional: The sequence of colors used, Default: DefaultColorSequence()
* ClassNames Optional: The names of the classes. Default: C1 - C(Number of Classes)
* PlotLegend Optional: Add a legent to plot. Default: TRUE)
* main Optional: Title of the plot. Default: "ClassBoxPlot""
* xlab Optional: Title of the x axis. Default: "Classes"
* ylab Optional: Title of the y axis. Default: "Data"

#### Value
A List of
ClassData The DataFrame used to plot
ggobject The ggplot2 plot object
in mode invisible
Author(s)
Michael Thrun, Felix Pape

#### Examples
```{r}
data(ITS)
model=AdaptGauss::AdaptGauss(ITS)
Classification=AdaptGauss::ClassifyByDecisionBoundaries(ITS,
DecisionBoundaries = AdaptGauss::BayesDecisionBoundaries(model$Means,model$SDs,model$Weights))
DataVisualizations::ClassBoxplot(ITS,Classification)$ggobject
```
