---
title: "``DataVisualizations::Crosstable``"
output: html_document
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(DataVisualizations)
```

Crosstable Crosstable plot
#### Description
Presents a heatmap with values and a cross table of given Data matrix of two features and a bin
width or percentualized values. In this approach the bin width is fixes. A more general way to
approach this is the kernel density estimation plot of PDEscatter.
#### Usage
<pre><code>
Crosstable(Data, xbins = seq(0, 100, 5), ybins = xbins,
NormalizationFactor = 1, PlotIt = TRUE, main='Cross Table',
PlotText=TRUE,TextDigits=0,TextProbs=c(0.05,0.95))
</code></pre>
#### Arguments
* Data [1:n,1:2] matrix of two features from which the cross table should be generated
from
xbins [1:k] start of k bins as a vector generated with seq of the first feature of data.
Default setting assumes percentiled values between zero and 100.
ybins [1:k] start of k bins as a vector generated with seq of the second feature of data.
Normally the same for both features, other settings are only possible if the length k is equal.
* NormalizationFactor
Optional, Data feautures can be seen as regular time series, e.g. 1 measurement
for a minute, in this case it is useful to normalize the output, e.g. to hours, then NormalizationFactor=60
PlotIt Optional, Plots the heatmap if TRUE. The first feature is on the x-axis (left to right) and the second on y-axis (bottom to top).
main In case of for PlotIt=TRUE: title of plot, see title
* PlotText In case of for PlotIt=TRUE: Default TRUE: plots text in heatmap with the values of the crosstable
* TextDigits In case of for TextDigits=TRUE: integer indicating the number of decimal places to use in round.
* TextProbs In case of for TextDigits=TRUE: [1:2] numeric vector of two probabilities defining the thresholds for white text to grey text and grey text to black text, e.g. below
the first threshold (Default 0.05) all values (5% of values) will be printed in white because the lowest values of the heatmap are blue. The second value of 0.95 works well if cross table has many zeros; uses quantile internally.

#### Details
The interval in each bin is closed to the left and opened to the right. The cross table can be seen as a two-dimensional histogram. The idea to add histograms to the table is taken from [Charpentier.2014].

#### Examples
```{r}
data(ITS)
data(MTY)
#simple but not a good transformation
Data=(cbind(ITS/max(ITS),MTY/max(MTY)))*100
#choice for bins could be better
Crosstable(Data)
```

#### Value
The cross table in invisible mode which depicts the number of values (frequency) in an specific
range with regard to two features.
The first feature is on the x-axis (left to right), and the second on y-axis (top to bottom) contrary to
the plot where it is bottom to top.
Note
For non percentiled values the PlotText part does not seem always to work, but I currently dont
know why the text does not always overlap with the heatmap.

#### Author(s)
Michael Thrun
References
[Charpentier. 2014] Charpentier, Arthur, ed. Computational actuarial science with R. CRC Press,
2014.
See Also
table, image, PDEscatter
