---
title: "``DataVisualizations::Fanplot``"
output: html_document
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(DataVisualizations)
```
Fanplot The fan plot

#### Description

The better alternative to the pie chart represents amount of values given in data.

#### Usage

<pre><code>
Fanplot(Datavector,Names,Labels,MaxNumberOfSlices,main='',col,
MaxPercentage=FALSE,ShrinkPies=0.05,Rline=1.1)
</code></pre>

#### Arguments

Datavector [1:n] a vector of n non unique values
Names Optional, [1:k] names to search for in Datavector, if not set unique of Datavector is calculated.
Labels Optional, [1:k] Labels if they are specially named, if not Names are used.
MaxNumberOfSlices
Default is k, integer value defining how many labels will be shown. Everything else will be summed up to Other.
main Optional, title below the fan pie, see plot
col Optional, default as other colors in this packages, else the same as in plot
MaxPercentage default FALSE; if true the biggest slice is 100 percent instead of the biggest procentual count
ShrinkPies Optional, distance between biggest and smallest slice of the pie
Rline Optional, the distance between text and pie is defined here as the length of the line in numerical numbers


#### Details
A normal pie plot is dificult to interpret for a human observer, because humans are not trained well
to observe angles [Gohil, 2015, p. 102]. Therefore, the fan plot is used. As proposed in [Gohil
2015] the fan.plot() of the plotrix package is used to solve this problem. If Number of Slices
is higher than MaxNumberOfSlices then ABCanalysis is applied (see [Ultsch/Lotsch, 2015]) and
group A chosen. If Number of Slices in group A is higher than MaxNumberOfSlices, then the most
important ones out of group A are chosen. If MaxNumberOfSlices is higher than Slices in group A,
additional slices are shown depending on the percentage (from high to low).

#### Value
silent output by calling invisible of a list with
Percentages [1:k] percent values visualized in fanplot
Labels [1:k] see input Labels, only relevant ones
Author(s)
Michael Thrun
References
[Gohil, 2015] Gohil, Atmajitsinh. R data Visualization cookbook. Packt Publishing Ltd, 2015.
[Ultsch/Lotsch, 2015] Ultsch. A ., Lotsch J.: Computed ABC Analysis for Rational Selection
of Most Informative Variables in Multivariate Data, PloS one, Vol. 10(6), pp. e0129767. doi
10.1371/journal.pone.0129767, 2015.

#### Examples
```{r}
data(categoricalVariable)
Fanplot(categoricalVariable)
```
