---
title: "``DataVisualizations::Heatmap``"
output: html_document
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(DataVisualizations)
```

Heatmap Heatmap for Clustering

#### Description
Heatmap of Distances of Data sorted by Cls

#### Usage
<pre><code>
Heatmap(DataOrDistances,Cls,method='euclidean',LowLim=0,HiLim)
</code></pre>

#### Arguments
* ``DataOrDistances``: [1:n,1:d] data cases in rows, variables in columns, if not symmetric or [1:n,1:n] distance matrix, if symmetric
* ``Cls``: numeric vector, [1:n,1] classified data
* ``method``: Optional, if Data[1:n,1:d] see dist for distance method
* ``LowLim``: Optional: limits for the color axis
* ``HiLim``: Optional: limits for the color axis


#### Examples
```{r}
data("Lsun3D")
Cls=Lsun3D$Cls
Data=Lsun3D$Data
Heatmap(as.matrix(dist(Data)),Cls = Cls)
```

#### Details
Clustering algorithms provide a Classifcation of data, where the labels are defined as a numeric vector Cls
Then, a typical cluster-respectively group structure is displayed by the HeatMap function. At the margin of the heatmap a dendrogram can be shown, if hierarchical cluster algorithms are used.
Here the dendrogram has to be shown separately and only the heatmap itself is displayed [Wilkinson,2009].
More details in [Thrun, 2018, p. 29]
Value
object of ggplot2

#### Author(s)
Michael Thrun

#### References
[Wilkinson,2009]Wilkinson, L., & Friendly, M.: The history of the cluster heat map, The American
Statistician, Vol. 63(2), pp. 179-184. 2009.
[Thrun, 2018] Thrun, M. C.: Projection Based Clustering through Self-Organization and Swarm
Intelligence, doctoral dissertation 2017, Springer, ISBN: 978-3-658-20539-3, Heidelberg, 2018.
26 inPSphere2D

