---
title: "``DataVisualizations::InspectDistances``"
output: html_document
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(DataVisualizations)
```

InspectDistances Inspection of Distance-Distribution

#### Description

Visualizes the distances between objects in the data matrix

#### Usage

<pre><code>
InspectDistances(DataOrDistances,method= "euclidean",sampleSize = 50000,...)
</code></pre>

#### Arguments
DataOrDistances
[1:n,1:d] data cases in rows, variables in columns, if not symmetric
or
[1:n,1:n] distance matrix, if symmetric
method Optional, if Data[1:n,1:d] see parallelDist::parDist for distance method
sampleSize double value defining the size of the sample for large distance matrizes, see
InspectVariable
... further arguments passed on to InspectVariable

#### Details
For an interpretation of the distribution analysis of the distance please read [Thrun, 2018, p. 27,
185].
Note
uses InspectVariable
Author(s)
Michael Thrun

#### References
[Thrun, 2018] Thrun, M. C.: Projection Based Clustering through Self-Organization and Swarm
Intelligence, doctoral dissertation 2017, Springer, ISBN: 978-3-658-20539-3, Heidelberg, 2018.

#### Examples
```{r}
data("Lsun3D")
Data=Lsun3D$Data
InspectDistances(as.matrix(dist(Data)))
```
