---
title: "``DataVisualizations::MAplot``"
output: html_document
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(DataVisualizations)
```

#### Description

Bland-Altman plot [Altman/Bland, 1983].

#### Usage
<pre><code>
MAplot(x,y,islog=TRUE,densityplot=FALSE,
main='MA-plot',xlab,ylab,Cls)
</code></pre>

#### Arguments
x [1:n] numerical vector of a feature/variable
y [1:n] another numerical vector of a feature/variable
islog TRUE: MAplot, FALSE: M=x-y versus a=0.5(x+y)
densityplot FALSE: Scatterplot, TRUE: density scatter plot with PDE
main see plot
xlab see plot
ylab see plot
Cls prior Classification as a numeric vector.

#### Examples
```{r}
#taken from [Thrun/Ultsch, 2018]
data("ITS")
data("MTY")
MAlist=MAplot(ITS,MTY)
```

Details
Bland-Altman plot [Altman/Bland, 1983] for visual representation of genomic data or in order to decorrelate data.

#### Value

MA [1:n,2] Matrix of Minus component of two features and Add component of two
features
ggplot see ggplot2 output, if densityplot=TRUE, else NULL
Author(s)
Michael Thrun
34 MDplot

#### References

* [Altman/Bland, 1983] Altman D.G., Bland J.M.: Measurement in medicine: the analysis of method
comparison studies, The Statistician, Vol. 32, p. 307-317, doi:10.2307/2987937, 1983.
* [Ultsch, 2005] Ultsch, A.: Pareto Density Estimation: A Density Estimation for Knowledge Discovery,
Baier D.,Wernecke K.D. (Eds), In Innovations in Classification, Data Science, and Information Systems - Proceedings 27th Annual Conference of the German Classification Society (GfKL) 2003,
Berlin, Heidelberg, Springer, pp, 91-100, 2005.

