---
title: "``DataVisualizations::MDplot``"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(DataVisualizations)
```

MDplot Mirrored Density plot (MD-plot)

#### Description

This function creates a MD-plot for each variable of the data matrix. The MD-plot is a visualization for a boxplot-like Shape of the PDF published in [Thrun/Ultsch, 2019]. It is an improvement of violin or so-called bean plots and posses advantages in comparison to the conventional well-known box plot [Thrun/Ultsch, 2019].

#### Usage

<pre><code>
MDplot(Data, Names, Ordering='Default', Scaling="None",
Fill='darkblue', RobustGaussian=TRUE, GaussianColor='magenta',
Gaussian_lwd=1.5, BoxPlot=FALSE, BoxColor='darkred',
MDscaling='width',Size=0.01, MinimalAmoutOfData=40,
MinimalAmoutOfUniqueData=12,SampleSize=5e+05,OnlyPlotOutput=TRUE)
</code></pre>

#### Arguments
* Data [1:n,1:d] Numerical Matrix containing the n cases of d variables. Each column is
one variable. A data.frame is automatically transformed to a numerical matrix.
* Names Optional: [1:d] Names of the variables. If missing, the columnnames of data are
used.
* ``Ordering`` Optional: string, either Default, Columnwise, Alphabetical or Statistics. Please see details for explanation.
* ``Scaling`` Optional, Default is None, Percentalize, CompleteRobust, Robust or Log, Please see details for explanation.
* ``Fill`` Optional: string, color with which MDs are to be filled with.
* ``RobustGaussian`` Optional: If TRUE: each MDplot of a variable is overlayed with a roubustly estimated unimodal Gaussian distribution in the range of this variable, if statistical
testing does not yield a significant p.value. In this case the packages moments, diptest and signal are required.
GaussianColor Optional: string, color of robustly estimated gaussian, only for RobustGaussian=TRUE.
Gaussian_lwd Optional: numerical, line width of robustly estimated gaussian, only for RobustGaussian=TRUE.
* ``BoxPlot``: Optional: If TRUE: each MDplot is overlayed with a Box-Whisker Diagram.
* ``BoxColor``: Optional: string, color of Boxplot, only for BoxPlot=TRUE.
* ``MDscaling``: Optional: if "area", all violins have the same area (before trimming the tails).
If "count", areas are scaled proportionally to the number of observations. If
"width" (default), all MDs have the same maximum width.
* Size Optional: numerical, linewidth of black line around the MDs.
* ``MinimalAmoutOfData`` Optional: numeric value defining a threshold. Below this threshold no density
estimation is performed and a Jitter plot with a median line is drawn. Only Data Science experts should change this value after they understand how the density is estimated (see [Ultsch, 2005]).
* ``MinimalAmoutOfUniqueData``: Optional: numeric value defining a threshold. Below this threshold no density
estimation and statistical testing is performed and a Jitter plot with a median line is drawn. Only Data Science experts should change this value after they understand how the density is estimated (see [Ultsch, 2005]).
* SampleSize Optional: numeric value defining a threshold. Above this threshold uniform
sampling of finite cases is performed in order to shorten computation time. If ``rowr`` is not installed, uniform sampling of all cases is performed. If required,
SampleSize=n can be set to omit this procedure.
* `OnlyPlotOutput``: Default TRUE only a ggplot object is given back, if FALSE: Additinally Scaled
Data and ordering are the output of this function in a list.

#### Examples
```{r}
x <- cbind(A = runif(20000, 1, 5), B = c(rnorm(10000,0,1),rnorm(10000,2.6,1)),
C = c(rnorm(20000,2.5,1)),D=rpois(20000,5))
MDplot(x)
```

#### Details
In short, the MD-plot can be described as a PDE optimized violin plot. The Pareto Density Estimation
(PDE) is an approach to estimate the probability density function (pdf) [Ultsch, 2005].
MD plot was used in [Thrun et al.,2018] for the evaluation of stochastic clustering methods and
used in [Thrun et al.,2018a] in order to simultaneously estimate variances of a high-dimensional
data set. The MD-plot is in the process of beeing peer-reviewed [Thrun/Ultsch, 2019].
Statistical testing is performed with dip.test and agostino.test.
For the paramter Ordering the following options are possible:
Default Ordering of plots by convex/concav/unimodal/nonunimodal shapes. In this case the signal
is required.

Columnwise Ordering of plots by the order of columns of Data.
Alphabetical Ordering of plots by the order of columns of Data sorted in alphabetical order by
column names.
Statistics Ordering of plots depending on the logarithm of the p-vlaues of statistical testing. In
this case the packages moments, diptest and signal are required.
For the paramter Scaling the following options are possible:
None No Scaling of data is done.
Percentalize Data is scaled between zero and 100.
CompleteRobust Data is first robustly scaled between zero and 1, then centered to zero and outliers
are capped by a robustly formula described in the DatabionicSwarm package.
Robust Data is robustly scaled between zero and 1 by a formula described in the Databionic-
Swarm package.
Log Data is transformed with a sgined log allowing for negative values to be transformed with a
logarithm of base 10, please see SignedLog for details.

#### Value

In the default case of OnlyPlotOutput==TRUE: The ggplot object of the MD-plot.
Otherwise for OnlyPlotOutput==FALSE: A list of
ggplotObj The ggplot object of the MD-plot.
Ordering The ordering of columns of data defined by Ordering.
DataOrdered [1:n,1:d] matrix of ordered and scaled data defined by Ordering and Scaling.
Note that the package ggExtra is not necessarily required but if given the feauture names are automatically
rotated.
Note
1.) One would assume that in the first of the two following cases ggplot only adjusts the plotting
region but:
MDplot(MTY)+ylim(c(0,7000)) is equal to MDplot(MTY[MTY<7000]).
This means in both cases the data is clipped and AFTERWARDS the density estimation is performed.
2.) Because of a (sometimes) strange behavior of either ggplot2 or reshape2, numerical column
names are changed to character by adding ’C_’.
3.) Overlaying MD-plots with robustly estimated gaussians seldomly will yield magenta (or other
GaussianColor) lines overlaying more than the violin plot they should overlay, because the width
of the two plots is not the same (but I am unable to set it strictly in ggplot). In such a case just call
the function again.

#### References

[Ultsch, 2005] Ultsch, A.: Pareto density estimation: A density estimation for knowledge discovery,
in Baier, D.; Werrnecke, K. D., (Eds), Innovations in classification, data science, and information
systems, Proc Gfkl 2003, pp 91-100, Springer, Berlin, 2005.
[Thrun/Ultsch, 2019] Thrun, M. C., & Ultsch, A. : Analyzing the Fine Structure of Distributions,
Technical Report prior to submission, Philipps-University Marburg, Germany, 2019.
[Thrun et al.,2018a] Thrun, M. C., Breuer, L., & Ultsch, A. : Knowledge discovery from lowfrequency
stream nitrate concentrations: hydrology and biology contributions, Proc. European
Conference on Data Analysis (ECDA), pp. 46-47, Paderborn, Germany, 2018.
[Thrun et al.,2018b] Thrun, M. C., Pape, F., & Ultsch, A. : Benchmarking Cluster Analysis Methods
using PDE-Optimized Violin Plots, Proc. European Conference on Data Analysis (ECDA), p. 26,
Paderborn, Germany, 2018.

Author(s)
Michael Thrun, Felix Pape contributed with the idea to use ggplot2 as the basic framework.
MDplot4multiplevectors 37
