---
title: "``DataVisualizations::PDEscatter``"
output: html_document
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(DataVisualizations)
```

PDEscatter Scatter Density Plot
#### Description
Pareto density estimation (PDE) [Ultsch, 2005] used for a scatter density plot.
#### Usage
<pre><code>
PDEscatter(x, y, na.rm = FALSE, paretoRadius = 0, sampleSize =
             round(sqrt(5e+08), -3), NrOfContourLines = 20, Plotter
           = "native", DrawTopView = T, xlab = "X", ylab = "Y",
           main = "PDEscatter", xlim, ylim, Legendlab_ggplot =
             "value")
</code></pre>
#### Arguments
* x Numeric vector, first feature (for x axis values)
* y Numeric vector, second feature (for y axis values)
* na.rm Function may not work with non finite values. If these cases should be automatically
removed, set parameter TRUE
* paretoRadius Numeric, the Pareto Radius. If omitted (or 0), calculate by paretoRad.
* ``sampleSize`` Numeric, maximum size of the sample used for calculation. High values increase
runtime significantly.
* ``NrOfContourLines``@
Numeric, number of contour lines to be drawn. 20 by default.
Plotter String, name of the plotting backend to use. Possible values are: "native", "ggplot",
"plotly"
DrawTopView Boolean, True means contur is drawn, otherwise a 3D plot is drawn. Default:
  True

* xlab String, title of the x axis. Default: "X", see plot() function
* ylab String, title of the y axis. Default: "Y", see plot() function
main string, the same as "main" in plot() function
* xlim see plot() function
* ylim see plot() function
* Legendlab_ggplot String, in case of Plotter="ggplot" label for the legend. Default: "value"

#### Details

The PDEscatter function generates the density of the xy data as a z coordinate. Afterwards xyz will be plotted either as a contour plot or a 3d plot. This function plots the PDE on top of a scatterplot.
Variances of x and y should not differ by extreme numbers, otherwise calculate the percentiles on both first. The method was succesfully used in [Thrun, 2018; Thrun/Ultsch 2018].


#### Examples
```{r}
#taken from [Thrun/Ultsch, 2018]
data("ITS")
data("MTY")
Inds=which(ITS<900&MTY<8000)
plot(ITS[Inds],MTY[Inds],main='Bimodality is not visible in normal scatter plot')
PDEscatter(ITS[Inds],MTY[Inds],xlab = 'ITS in EUR',
           ylab ='MTY in EUR' ,main='Pareto Density Estimation indicates Bimodality' )
```


#### Value
List of:
  AnzInPSpheres Number of points within the ParetoRadius of each point
ParetoRadius ParetoRadius used for PDEscatter
Handle Handle of the plot object. Information-string if native R plot is used.
Note
If DrawTopView=FALSE only the plotly option is currently available. If another option is chosen, the
method switches automatically there.

#### Author(s)
Felix Pape
References
[Thrun, 2018] Thrun, M. C.: Projection Based Clustering through Self-Organization and Swarm
Intelligence, (Ultsch, A. & Huellermeier, E. Eds., 10.1007/978-3-658-20540-9), Doctoral dissertation,
Heidelberg, Springer, ISBN: 978-3658205393, 2018.
[Thrun/Ultsch, 2018] Thrun, M. C., & Ultsch, A. : Effects of the payout system of income taxes
to municipalities in Germany, in Papiez, M. & Smiech„ S. (eds.), Proc. 12th Professor Aleksander
Zelias International Conference on Modelling and Forecasting of Socio-Economic Phenomena, pp.
533-542, Cracow: Foundation of the Cracow University of Economics, Cracow, Poland, 2018.
[Ultsch, 2005] Ultsch, A.: Pareto density estimation: A density estimation for knowledge discovery,
In Baier, D. & Werrnecke, K. D. (Eds.), Innovations in classification, data science, and information
systems, (Vol. 27, pp. 91-100), Berlin, Germany, Springer, 2005.
