---
title: "``DataVisualizations::PlotMissingvalues ``"
output: html_document
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(DataVisualizations)
```
## ``PlotMissingvalues``
Plot of the Amount Of Missing Values
#### Description
Percentage of missing values per feature are visualized as a bar plot.
#### Usage
<pre><code>
PlotMissingvalues(Data,Names,
                  WhichDefineMissing=c('NA','DUMMY','.',' '),
                  PlotIt=TRUE,xlab='Amount Of Missing Values in percent',...)
</code></pre>
#### Arguments
* Data [1:n,1:d] data cases in rows, variables/features in columns
* Names [1:d] optional vector of string describing the names of the features
WhichDefineMissing
[1:d] optional vector of string describing missing values, usefull for character
features.
PlotIt If FALES: Does not plot
* xlab x label of bar plot
* ... Further #### Arguments passed on to barplot, such as main for title



#### Examples
```{r}
data("ITS")
data("MTY")
PlotMissingvalues(cbind(ITS,MTY),Names=c('ITS','MTY'))
PlotProductratio 49
```

#### Value
plots not finite and missing values as a bar plot for each feature d and returns with invisible the
amount of missing values as a vector. Works even with character variables, but WhichDefineMissing
cannot be changed at the current version. Please make a suggestion on GitHub how to improve
this.
Note
Does not work with the tibble format, in such a case please call as.data.frame(as.matrix(Data))
Author(s)
Michael Thrun
