---
title: "``DataVisualizations::``"
output: html_document
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(DataVisualizations)
```
PlotProductratio Product-Ratio Plot
#### Description
The product-ratio plot as defined in [Tukey, 1977, p. 594].

#### Usage
<pre><code>
PlotProductratio(x, y, na.rm = FALSE,
                 main='Product Ratio Analysis',xlab = "Log of Ratio",ylab = "Root of Product", ...)
</code></pre>
#### Arguments
x [1:n] positive numerical vector, negativ values are removed automatically
y [1:n] positive numerical vector, negativ values are removed automatically
na.rm Function may not work with non finite values. If these cases should be automatically
removed, set parameter TRUE
main see plot
ylab see plot
xlab see plot
... further arguments passed on to plot

#### Examples
```{r}
#Beware: The data does no fit ne requirements for this approach
data('ITS')
data(MTY)
PlotProductratio(ITS,MTY)
50 QQplot
```

#### Details
In the case where there are many instances of very small values, but a small number of very large
ones, this plot is usefull [Tukey, 1977, p. 615].
Value
matrix[1:n,2] with sqrt(x*y) and log(x/y) as the two columns
Author(s)
Michael Thrun
References
[Tukey, 1977] Tukey, J. W.: Exploratory data analysis, United States Addison-Wesley Publishing
Company, ISBN: 0-201-07616-0, 1977.
