---
title: "``DataVisualizations::Plot3D``"
output: html_document
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(DataVisualizations)
```


Plot3D 3D plot of points
#### Description
A wrapper for Data with systematic clustering colors for either a 2D (x,y) or 3D (x,y,z) plot combined
with a classification
#### Usage
<pre><code>
Plot3D(Data,Cls,UniqueColors,size=2,na.rm=FALSE,...)
</code></pre>

#### Arguments
* Data [1:n,1:d] matrix with either d=2 or d=3, if d>3 only the first 3 dimensions are taken
* Cls [1:n] numeric vector of the classification of data with k classes
* ``UniqueColors`` [1:k] character vector of colors, if not given ``DataVisualizations::DefaultColorSequence`` is used
* ``size``: size of points
* ``na.rm``: if na.rm=TRUE, then missing values are removed
* ``...``: further arguments to be processed by plot3d or geom_point

#### Details
For geom_point only size and na.rm is available as further arguments.

#### Examples
```{r}
#Spin3D similar output
data(Lsun3D)
Plot3D(Lsun3D$Data,Lsun3D$Cls,type='s',radius=0.1,box=FALSE,aspect=TRUE)
rgl::grid3d(c("x", "y", "z"))
#Projected Points with Classification
Data=cbind(runif(500,min=-3,max=3),rnorm(500))
```
```{r}
# Classification
Cls=ifelse(Data[,1]>0,1,2)
Plot3D(Data,Cls,UniqueColors = DataVisualizations::DefaultColorSequence[c(1,3)],size=2)
#Points with Non-Overlapping Labels
#require(ggrepel)
Data=cbind(runif(30,min=-1,max=1),rnorm(30,0,0.5))
Names=paste0('VeryLongName',1:30)
ggobj=Plot3D(Data)
ggobj + geom_text_repel(aes(label=Names), size=3)
```

Note
Uses either geom_point for 2D or plot3d for 3D
Author(s)
Michael Thrun
References
RGL vignette in https://cran.r-project.org/package=rgl
Spin3D in https://www.uni-marburg.de/fb12/arbeitsgruppen/datenbionik/software-en
