---
title: "``DataVisualizations::ShepardPDEscatter``"
output: html_document
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(DataVisualizations)
```

ShepardPDEscatter Shepard PDE scatter
#### Description
Draws ein Shepard Diagram (scatterplot of distances) with an two-dimensional PDE density estimation
.
#### Usage

<pre><code>
ShepardPDEscatter(InputDists, OutputDists, Plotter = "native",
  xlab ="Input Distances", ylab = "Output Distances",
  main = "ProjectionMethod",sampleSize)
</code></pre>

#### Arguments

* ``InputDists``: [1:n,1:n] with n cases of data in d variables/features: Matrix containing the distances
of the inputspace.
* ``OutputDists``: [1:n,1:n] with n cases of data in d dimensionalites of the projection method
* ``variables/features``: Matrix containing the distances of the outputspace.
* ``xlab``: Label of the x axis in the resulting Plot.
* ``ylab``: Label of the y axis in the resulting Plot.
* ``Plotter``: see PDEscatter for details
* ``main``: Title of the Shepard diagram
* ``sampleSize``: Optional, default(50000), reduces a.ount of data for density estimation, if too many distances given

#### Examples
```{r}
data("Lsun3D")
Cls=Lsun3D$Cls
Data=Lsun3D$Data
InputDist=as.matrix(dist(Data))
res = stats::cmdscale(d = InputDist, k = 2, eig = TRUE,
add = FALSE, x.ret = FALSE)
ProjectedPoints = as.matrix(res$points)
ShepardPDEscatter(InputDist,as.matrix(dist(ProjectedPoints)),main = 'MDS')
```

#### References

[Thrun, 2018] Thrun, M. C.: Projection Based Clustering through Self-Organization and Swarm
Intelligence, doctoral dissertation 2017, Springer, ISBN: 978-3-658-20540-9, Heidelberg, 2018.

#### Details
Introduced and described in [Thrun, 2018, p. 63] with examples in [Thrun, 2018, p. 71-72]

#### Author(s)
Michael Thrun
