---
title: "``gdata::case```"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(gdata)
```

Map elements of a vector according to the provided ’cases’

#### Description

Map elements of a vector according to the provided ’cases’. This function is useful for mapping
discrete values to factor labels and is the vector equivalent to the switch function.

#### Usage
<pre><code>

case(x, ..., default = NA)

</code></pre>
#### Arguments

* x Vector to be converted
* ... Map of alternatives, specified as "name"=value default value to be assigned to elements of x not matching any of the alternatives. Defaults to NA.


#### Examples
```{r}

## default = NA
case( c(1,1,4,3), "a"=1, "b"=2, "c"=3)
## default = "foo"
case( c(1,1,4,3), "a"=1, "b"=2, "c"=3, default="foo" )
````
#### Details

This function is to switch what ifelse is to if, and is a convenience wrapper for factor.

#### Value

A factor variables with each element of x mapped into the corresponding level of specified in the
mapping.
Author(s)
Gregory R. Warnes <greg@warnes.net>
See Also
factor, switch, ifelse




