---
title: "``gdata::centerText``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(gdata)
```

Center Text Strings

#### Description

Function to center text strings for display on the text console by prepending the necessary number
of spaces to each element.

#### Usage
<pre><code>

centerText(x, width = getOption("width"))

</code></pre>
#### Arguments

x
width
Character vector containing text strings to be centered.
Desired display width. Defaults to the R display width given by getOption("width").

#### Details

Each element will be centered individually by prepending the necessary number of spaces to center
the text in the specified display width assuming a fixed width font.

#### Value

Vector of character strings.
Author(s)
Gregory R. Warnes <greg@warnes.net>
See Also
strwrap

#### Examples
```{r}

cat(centerText("One Line Test"), "\n\n")
mText <-c("This", "is an example",
" of a multiline text
",
"with ",
"
leading",
" and trailing
",
"spaces.")
cat("\n", centerText(mText), "\n", sep="\n")
```     



