---
title: "``gdata::drop.levels``"
output: html_document
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(gdata)
```


#### Description

Drop unused levels in a factor

#### Usage
<pre><code>

drop.levels(x, reorder=TRUE, ...)

</code></pre>
#### Arguments

* x object to be processed
* reorder should factor levels be reordered using reorder.factor?
* ... additional arguments to reorder.factor

#### Details

drop.levels is a generic function, where default method does nothing, while method for factor s
drops all unused levels. Drop is done with x[, drop=TRUE].
There are also convenient methods for list and data.frame, where all unused levels are dropped
in all factors (one by one) in a list or a data.frame.

#### Value

Input object without unused levels.
Author(s)
Jim Rogers <james.a.rogers@pfizer.com> and Gregor Gorjanc

#### Examples
```{r}

f <- factor(c("A", "B", "C", "D"))[1:3]
drop.levels(f)
l <- list(f=f, i=1:3, c=c("A", "B", "D"))
drop.levels(l)
df <- as.data.frame(l)
str(df)
str(drop.levels(df))
```
