---
title: "``gdata::elem``"
output: html_document
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(gdata)
```

Display Information about Elements in a Given Object

#### Description

This function is depreciated. Please use ll instead.
Display name, class, size, and dimensions of each element in a given object.

#### Usage
<pre><code>

elem(object=1, unit=c("KB","MB","bytes"), digits=0,
dimensions=FALSE)

</code></pre>
#### Arguments

* object object containing named elements, perhaps a model or data frame.
* unit required unit for displaying element size: "KB", "MB", "bytes", or first letter.
* digits number of decimals to display when rounding element size.
* dimensions whether element dimensions should be returned.

#### Details

A verbose alternative to names().

#### Value

A data frame with named rows and the following columns:
Class element class.
KB element size (see notes).
Dim element dimensions (optional).
Note
The name of the element size column is the same as the unit used.
Elements of class classRepresentation, ClassUnionRepresentation, and grob do not have a
defined size, so 0 bytes are assumed for those.env
15
Author(s)
Arni Magnusson <arnima@u.washington.edu>
See Also
names, str, and summary display different information about object elements.
ll and env are related to elem.

#### Examples
```{r}

## Not run:
data(infert)
elem(infert)
model <- glm(case~spontaneous+induced, family=binomial, data=infert)
elem(model, dim=TRUE)
elem(model$family)
## End(Not run)
```
