---
title: "``gdata::first``"
output: html_document
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(gdata)
```

return first or last element of an object

#### Description

Return first or last element of an object. These functions are convenience wrappers for head(x, n=1, ...) and tail(x, n=1, ...).

#### Usage
<pre><code>

first(x, n=1, ...)
last(x, n=1, ...)
first(x, n=1, ...) <- value
last(x, n=1, ...) <- value

</code></pre>
#### Arguments

* ``x ``: data object
n a single integer. If positive, size for the resulting object: number of elements for a vector (including lists), rows for a matrix or data frame or lines for a function.
If negative, all but the ’n’ last/first number of elements of ’x’.
* ... arguments to be passed to or from other methods.
* ``value`` a vector of values to be assigned (should be of length n)

#### Value

An object (usually) like ’x’ but generally smaller.
Author(s)
Gregory R. Warnes <greg@warnes.net>frameApply
17
See Also
head, tail, left, right

#### Examples
```{r}

## works for vectors..
v <- 1:10
first(v)
last(v)
first(v) <- 9
v
last(v) <- 20
v
## and for lists
l <- list(a=1, b=2, c=3)
first(l)
last(l)
first(l) <- "apple"
last(l) <- "bannana"
l
## and data.frames
df <- data.frame(a=1:2, b=3:4, c=5:6)
first(df)
last(df)
first(df) <- factor(c("red","green"))
last(df) <- list(c(20,30)) # note the enclosing list!
df
## and matrixes
m <- as.matrix(df)
first(m)
last(m)
first(m) <- "z"
last(m) <- "q"
m
```
