---
title: "``gdata::getYear``"
output: html_document
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(gdata)
```

Get date/time parts from date and time objects

#### Description

get* functions provide an *experimental* approach for extracting the date/time parts from objects of a date/time class. They are designed to be intiutive and thus lowering the learning curve for work with date and time classes in R.

#### Usage
<pre><code>

getYear(x, format, ...)
getMonth(x, format, ...)
getDay(x, format, ...)
getHour(x, format, ...)
getMin(x, format, ...)
getSec(x, format, ...)

</code></pre>
#### Arguments

x generic, date/time object
format character, format
... arguments pased to other methods

#### Value

Character
Author(s)
Gregor Gorjanc
See Also
Date, DateTimeClasses, strptime

#### Examples
```{r}

## --- Date class ---
tmp <- Sys.Date()
tmp
getYear(tmp)
getMonth(tmp)humanReadable
21
getDay(tmp)
## --- POSIXct class ---
tmp <- as.POSIXct(tmp)
getYear(tmp)
getMonth(tmp)
getDay(tmp)
## --- POSIXlt class ---
tmp <- as.POSIXlt(tmp)
getYear(tmp)
getMonth(tmp)
getDay(tmp)
```
