---
title: "``gdata::humanReadable```"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(gdata)
```

Print Byte Size in Human Readable Format

#### Description

humanReadable converts integer byte sizes to a human readable units such as kB, MB, GB, etc.

#### Usage
<pre><code>

humanReadable(x, units="auto", standard=c("IEC", "SI", "Unix"),
digits=1, width=NULL, sep=" ", justify=c("right", "left") )

</code></pre>
#### Arguments

* x integer, byte size
* standard character, "IEC" for powers of 1024 (’MiB’), "SI" for powers of 1000 (’MB’),
or "Unix" for powers of 1024 (’M’). See details.
* units character, unit to use for all values (optional), one of "auto", "bytes", or an appropriate unit corresponding to standard.
* digits integer, number of digits after decimal point
* width integer, width of number string
* sep character, separator between number and unit
* justify two-element vector specifiy the alignment for the number and unit components of the size. Each element should be one of "none", "left", "right", or "center"


#### Examples
```{r}

# Simple example: maximum addressible size of 32 bit pointer
humanReadable(2^32-1)
humanReadable(2^32-1, standard="IEC")
humanReadable(2^32-1, standard="SI")
humanReadable(2^32-1, standard="Unix")
humanReadable(2^32-1,
humanReadable(2^32-1,
humanReadable(2^32-1,
humanReadable(2^32-1,
unit="MiB")
standard="IEC", unit="MiB")
standard="SI", unit="MB")
standard="Unix", unit="M")
# Vector of sizes
matrix(humanReadable(c(60810, 124141, 124, 13412513), width=4))
matrix(humanReadable(c(60810, 124141, 124, 13412513), width=4, unit="KiB"))
# Specify digits rather than width
matrix(humanReadable(c(60810, 124141, 124, 13412513), width=NULL, digits=2))
# Change the justification
matrix(humanReadable(c(60810, 124141, 124, 13412513), width=NULL,
justify=c("right", "right") ))
```

#### Details

The basic unit used to store information in computers is a bit. Bits are represented as zeroes and ones - binary number system. Although, the binary number system is not the same as the decimal
number system, decimal prefixes for binary multiples such as kilo and mega are often used. In the decimal system kilo represent 1000, which is close to 1024 = 2 10 in the binary system. This
sometimes causes problems as it is not clear which powers (2 or 10) are used in a notation like 1 kB. To overcome this problem International Electrotechnical Commission (IEC) has provided the
following solution to this problem:

Name
byte
kilobyte
kibibyte
megabyte
mebibyte
gigabyte
gibibyte
terabyte
tebibyte
petabyte
pebibyte
exabyte
exbibyte
zettabyte
zebibyte
yottabyte
yebibyte
System
binary
decimal
binary
decimal
binary
decimal
binary
decimal
binary
decimal
binary
decimal
binary
decimal
binary
decimal
binary
Symbol
B
kB
KiB
MB
MiB
GB
GiB
TB
TiB
PB
PiB
EB
EiB
ZB
ZiB
YB
YiB
Size
2 3
10 3
2 10
(10 3 ) 2
(2 10 ) 2
(10 3 ) 3
(2 10 ) 3
(10 3 ) 4
(2 10 ) 4
(10 3 ) 5
(2 10 ) 5
(10 3 ) 6
(2 10 ) 6
(10 3 ) 7
(2 10 ) 7
(10 3 ) 8
(2 10 ) 8
Conversion
8 bits
1000 bytes
1024 bytes
1000 kilobytes
1024 kibibytes
1000 megabytes
1024 mebibytes
1000 gigabytes
1024 gibibytes
1000 terabytes
1024 tebibytes
1000 petabytes
1024 pebibytes
1000 exabytes
1024 exbibytes
1000 zettabytes
1024 zebibytes
where Zi and Yi are GNU extensions to IEC. To get the output in the decimal system (powers of
1000) use standard="SI". To obtain IEC standard (powers of 1024) use standard="IEC".
In addition, single-character units are provided that follow (and extend) the Unix pattern (use
standard="Unix"):
Name
byte
kibibyte
mebibyte
gibibyte
tebibyte
pebibyte
exbibyte
zebibyte
yottabyte
System
binary
binary
binary
binary
binary
binary
binary
binary
binary
Symbo.
P
E
Z
Y
Size
2 3
2 10
(2 10 ) 2
(2 10 ) 3
(2 10 ) 4
(2 10 ) 5
(2 10 ) 6
(2 10 ) 7
(2 10 ) 8
Conversion
8 bits
1024 bytes
1024 kibibytes
1024 mebibytes
1024 gibibytes
1024 tebibytes
1024 pebibytes
1024 exbibytes
1024 zebibytes
For printout both digits and width can be specified. If width is NULL, all values have givenhumanReadable
23
number of digits. If width is not NULL, output is rounded to a given width and formated similar to
human readable format of the Unix ls, df or du shell commands.

#### Value

Byte size in human readable format as character with proper unit symbols added at the end of the
string.
Author(s)
Ales Korosec, Gregor Gorjanc, and Gregory R. Warnes <greg@warnes.net>
References
Wikipedia: http://en.wikipedia.org/wiki/Byte http://en.wikipedia.org/wiki/SI_prefix
http://en.wikipedia.org/wiki/Binary_prefix
GNU manual for coreutils: http://www.gnu.org/software/coreutils/manual/html_node/Block-size.
html#Block-size
See Also
object.size in package ’gdata’, object.size in package ’utils’, ll
