---
title: "``gdata::interleave``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(gdata)
```


#### Description

Interleave rows of data frames or Matrices.

#### Usage
<pre><code>

interleave(..., append.source=TRUE, sep=": ", drop=FALSE)

</code></pre>
#### Arguments

* ... objects to be interleaved
* append.source Boolean Flag. When TRUE (the default) the argument name will be appended to the row names to show the source of each row.
* ``sep``: Separator between the original row name and the object name.
* drop boolean flag - When TRUE, matrices containing one column will be converted to vectors.


#### Examples
```{r}

# Simple example
a <- matrix(1:10,ncol=2,byrow=TRUE)
b <- matrix(letters[1:10],ncol=2,byrow=TRUE)
c <- matrix(LETTERS[1:10],ncol=2,byrow=TRUE)
interleave(a,b,c)
# Useful example:
#
# Create a 2-way table of means, standard errors, and # obs
g1 <- sample(letters[1:5], 1000, replace=TRUE)
g2 <- sample(LETTERS[1:3], 1000, replace=TRUE )
dat <- rnorm(1000)
stderr <- function(x) sqrt( var(x,na.rm=TRUE) / nobs(x) )
means
<- tapply(dat,
stderrs <- tapply(dat,
ns
<- tapply(dat,
blanks <- matrix( " ",
list(g1, g2), mean )
list(g1, g2), stderr )
list(g1, g2), nobs )
nrow=5, ncol=3)
tab <- interleave( "Mean"=round(means,2),
"Std Err"=round(stderrs,2),
"N"=ns, " " = blanks, sep=" " )
print(tab, quote=FALSE)
# Using drop to control coercion to a lower dimensions:
m1 <- matrix(1:4)
m2 <- matrix(5:8)
interleave(m1, m2, drop=TRUE)
# This will be coerced to a vector
interleave(m1, m2, drop=FALSE) # This will remain a matrix
```
#### Details

This function creates a new matrix or data frame from its arguments.
The new object will have all of the rows from the source objects interleaved. IE, it will contain row
1 of object 1, followed by row 1 of object 2, .. row 1 of object ’n’, row 2 of object 1, row 2 of object
2, ... row 2 of object ’n’ ...

#### Value

Matrix containing the interleaved rows of the function arguments.
Author(s)
Gregory R. Warnes <greg@warnes.net>26
is.what
See Also
cbind, rbind, combine
