---
title: "``gdata::ll``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
ll
Describe Objects or Elements

#### Description

Display name, class, size, and dimensions of each object in a given environment. Alternatively, if the main argument is a list-like object, its elements are listed and described.

#### Usage
<pre><code>

ll(pos=1, unit="KB", digits=0, dim=FALSE, sort=FALSE, class=NULL, invert=FALSE, ...)

</code></pre>
#### Arguments

* ``pos``: environment position number, environment name, data frame, list, model, or any object that is.list.
* ``unit``: unit for displaying object size: "bytes", "KB", "MB", or first letter.
* ``digits``: number of decimals to display when rounding object size.
* ``dim``: whether object dimensions should be returned.
* ``sort``: whether elements should be sorted by name.
* ``class``: character vector for limiting the output to specified classes.
* ``invert``: whether to invert the class filter, so specified classes are excluded.
* ``...``: passed to ls.

#### Value

A data frame with named rows and the following columns:
* ``Class``: object class.
KB object size (see note).
Dim object dimensions (optional).
Note
The name of the object size column is the same as the unit used.

#### Author(s)
Arni Magnusson, with a contribution by Jim Rogers
See Also
ll is a verbose alternative to ls (objects in an environment) and names (elements in a list-like object).
str and summary also describe elements in a list-like objects.
env is a related function that describes all loaded environments.

#### Examples
```{r}

ll()
ll(all=TRUE)
ll("package:base")
ll("package:base", class="function", invert=TRUE)
data(infert)
ll(infert)
model <- glm(case~spontaneous+induced, family=binomial, data=infert)
ll(model, dim=TRUE)
ll(model, sort=TRUE)
ll(model$family)
```
