---
title: "gdata::MedUnits"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#### Description

Table of conversions between Intertional Standard (SI) and US ’Conventional’ Units for common
medical measurements.

#### Usage
<pre><code>

data(MedUnits)
</code></pre>

#### Format
A data frame with the following 5 variables.
* Abbreviation Common Abbreviation (mostly missing)
* Measurement Measurement Name
* ConventionalUnit Conventional Unit
* Conversion Conversion factor
* SIUnit SI Unit

#### Details

Medical laboratories and practitioners in the United States use one set of units (the so-called ’Conventional’ units) for reporting the results of clinical laboratory measurements, while the rest of the
world uses the International Standard (SI) units. It often becomes necessary to translate between these units when participating in international collaborations.
This data set provides constants for converting between SI and US ’Conventional’ units.
To perform the conversion from SI units to US ’Conventional’ units do:
Measurement in ConventionalUnit = (Measurement in SIUnit) / Conversion
To perform conversion from ’Conventional’ to SI units do:
Measurement in SIUnit = (Measurement in ConventionalUnit) * Conversion

#### Source
http://www.globalrph.com/conv_si.htm
See Also
The function ConvertMedUnits automates the conversion task.mv
37

#### Examples
```{r}

data(MedUnits)
# show available conversions
MedUnits$Measurement
# utility function
matchUnits <- function(X) MedUnits[ grep(X, MedUnits$Measurement),]
# Convert SI Glucose measurement to 'Conventional' units
GlucoseSI = c(5, 5.4, 5, 5.1, 5.6, 5.1, 4.9, 5.2, 5.5) # in SI Units
GlucoseUS = GlucoseSI / matchUnits("Glucose")$Conversion
cbind(GlucoseSI,GlucoseUS)
# also consider using ConvertMedUnits()
ConvertMedUnits( GlucoseSI, "Glucose", to="US" )
```
