---
title: "``gdata::nobs``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Compute the Number of Non-missing Observations

#### Description

Compute the number of non-missing observations. Provides a ’default’ method to handle vectors, and a method for data frames.

#### Usage
<pre><code>

nobs(object, ...)
## Default S3 method:
nobs(object, ...)
## S3 method for class 'data.frame'
nobs(object, ...)
## S3 method for class 'lm'
nobs(object, ...)

</code></pre>
#### Arguments

object Target Object
... Optional parameters (currently ignored)

#### Details

Calculate the number of observations in object.
• For numeric vectors, this is simply the number of non-NA elements, as computed by sum(!is.na(object)).
• For dataframe objects, the result is a vector containing the number of non-NA elementes of each column.
The nobs and nobs.lm functions defined in gtools are simply aliases for the functions in the base R stats package, provided for backwards compatibility.nPairs
39

#### Value

Either single numeric value (for vectors) or a vector of numeric values (for data.frames) giving the number of non-missing values.
Note
The base R package stats now provides a S3 dispatch function for nobs, and methods for for objects of classes "lm", "glm", "nls" and "logLik", as well as a default method.
Since they provided a subset of the the functionality, the base method dispatch (nobs) function and method for "lm" objects (nobs.lm) are, as of gdata version 2.10.1, simply aliases for the equivalent
functions in the base R stats package.
Since gdata’s default method (nobs.default) processes vectors and hands any other data/object types to stats:::nobs.default.

#### Author(s)
Gregory R. Warnes <greg@warnes.net>
See Also
is.na, length

#### Examples
```{r}

x <- c(1,2,3,5,NA,6,7,1,NA )
length(x)
nobs(x)
df <- data.frame(x=rnorm(100), y=rnorm(100))
df[1,1] <- NA
df[1,2] <- NA
df[2,1] <- NA
nobs(df)
fit <- lm(y ~ x, data=df)
nobs(fit)
```
