---
title: "``gdata::nPairs``"
output: html_document
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#### Description

``nPairs()`` counts the number of pairs between variables.

#### Usage
<pre><code>
  
  nPairs(x, margin=FALSE, names=TRUE, abbrev=TRUE, ...)

</code></pre>

#### Arguments
  
* ``x``: data.frame or a matrix
* ``margin``: logical, calculate the cumulative number of “pairs”
* ``names``: logical, add row/col-names to the output
* ``abbrev``: logical, abbreviate names
... ot* ``...``: arguments passed to abbreviate


#### Examples
```{r}

## Test data
test <- data.frame(V1=c(1, 2, 3, 4, 5),
                   V2=c(NA, 2, 3, 4, 5),
                   V3=c(1, NA, NA, NA, NA),
                   V4=c(1, 2, 3, NA, NA))
## Number of variable pairs
nPairs(x=test)
## Without names
nPairs(x=test, names=FALSE)
```

```{r}
## Longer names
colnames(test) <- c("Variable1", "Variable2", "Variable3", "Variable4")
nPairs(x=test)
## Margin
nPairs(x=test, margin=TRUE)
## Summaryobject.
summary(object=nPairs(x=test))
```

#### Details

The class of returned matrix is nPairs and matrix. There is a summary method, which shows the opposite information - counts how many times each variable is known, while the other variable of a pair is not. See examples.

#### Value

Matrix of order k, where k is the number of columns in x. 
Values in a matrix represent the number of pairs between columns/variables in x. 
If margin=TRUE, the number of columns is k + 1 and the last column represents the cumulative number of pairing all variables.

#### Author(s)
Gregor Gorjanc

