---
title: "``gdata::object.size``"
output: html_document
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Report the Space Allocated for Objects

#### Description

Provides an estimate of the memory that is being used to store R objects.

#### Usage
<pre><code>
  
  object.size(...)
## S3 method for class 'object_sizes'
is(x)
## S3 method for class 'object_sizes'
as(x)
## S3 method for class 'object_sizes'
c(..., recursive=FALSE)
## S3 method for class 'object_sizes'
format(x, humanReadable=getOption("humanReadable"), standard="IEC", units,
       digits=1, width=NULL, sep=" ", justify = c("right", "left"), ...)
## S3 method for class 'object_sizes'
print(x, quote=FALSE, humanReadable=getOption("humanReadable"),
      standard="IEC", units, digits=1, width=NULL, sep=" ",
      justify = c("right", "left"), ...)

</code></pre>
  #### Arguments
  
  * ... object.size: R objects; print and format: arguments to be passed to other methods.
* x output from object.size
* quote logical, indicating whether or not the result should be printed with surrounding quotes.
* humanReadable logical, use the “human readable” format.
* standard,units,digits,width,sep,justify
See the man page for humanReadable.
recursive
See the man page for c.42
object.size

#### Details

This is a modified copy of the man page for utils::object.size in R 2.2.1.
Exactly which parts of the memory allocation should be attributed to which object is not clear-cut. This function merely provides a rough indication: it should be reasonably accurate for atomic
vectors, but does not detect if elements of a list are shared, for example. (Sharing amongst elements of a character vector is taken into account, but not that between character vectors in a single object.)
The calculation is of the size of the object, and excludes the space needed to store its name in the symbol table.
Associated space (e.g., the environment of a function and what the pointer in a EXTPTRSXP points to) is not included in the calculation.
Object sizes are larger on 64-bit builds than 32-bit ones, but will very likely be the same on different platforms with the same word length and pointer size.
Changes
Class of returned object is c("object_sizes", "numeric") with appropriate print and c methods.
By default object.size outputs size in bytes, but human readable format similar to ls, df or du shell commands can be displayed by calling humanReadable directly, calling print with the
argument humanReadable=TRUE, or by setting options(humanReadable=TRUE).

#### Value

A numeric vector class c("object_sizes", "numeric") containing estimated memory allocation
attributable to the objects in bytes.
See Also
object.size in package ’utils’ for the standard version of this function, Memory-limits for the
design limitations on object size, humanReadable for human readable format.

#### Examples
```{r}

object.size(letters)
object.size(ls)
## find the 10 largest objects in the base package
allObj <- sapply(ls("package:base"),
                 function(x)
                   object.size(get(x, envir = baseenv()))
)
( bigObj <- as.object_sizes(rev(sort(allObj))[1:10] ) )
print(bigObj, humanReadable=TRUE)
as.object_sizes(14567567)
options(humanReadable=TRUE)read.xls
(
  43
  z <- object.size(letters,
                   c(letters, letters),
                   rep(letters, 100),
                   rep(letters, 10000)
  )
)
is.object_sizes(z)
as.object_sizes(14567567)
```

