
---
title: "``gdata::rename.vars``"
output: html_document
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(gdata)
```


#### Description

Remove or rename a variables in a data frame.

#### Usage
<pre><code>

rename.vars(data, from="", to="", info=TRUE)
remove.vars(data, names="", info=TRUE)

</code></pre>
#### Arguments

* data dataframe to be modified.
* from character vector containing the current name of each variable to be renamed.
* to character vector containing the new name of each variable to be renamed.
* names character vector containing the names of variables to be removed.
* info boolean value indicating whether to print details of the removal/renaming. Defaults to TRUE.

#### Value

The updated data frame with variables listed in from renamed to the corresponding element of to.reorder.factor
47
Author(s)
Code by Don MacQueen <macq\@llnl.gov>. Documentation by Gregory R. Warnes <greg@warnes.net>
See Also
names, colnames, data.frame

#### Examples
```{r}

data <- data.frame(x=1:10,y=1:10,z=1:10)
names(data)
data <- rename.vars(data, c("x","y","z"), c("first","second","third"))
names(data)
data <- remove.vars(data, "second")
names(data)
```


         
