
---
title: "``gdata::reorder.factor``"
output: html_document
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(gdata)
```

#### Description

Reorder the levels of a factor

#### Usage
<pre><code>

## S3 method for class 'factor'
reorder(x, X, FUN, ..., order=is.ordered(x), new.order, sort=mixedsort)

</code></pre>
#### Arguments

* ``x``: factor
* X auxillary data vector
* FUN function to be applied to subsets of X determined by x, to determine factor order
* ... optional parameters to FUN
* ``order``: logical value indicating whether the returned object should be an ordered factor
* ``new.order``: a vector of indexes or a vector of label names giving the order of the new factor levels
* ``sort``: function to use to sort the factor level names, used only when new.order is missing

#### Details

This function changes the order of the levels of a factor. It can do so via three different mechanisms,
depending on whether, X and FUN, new.order or sort are provided.
If X and Fun are provided: The data in X is grouped by the levels of x and FUN is applied. The groups
are then sorted by this value, and the resulting order is used for the new factor level names.
If new.order is a numeric vector, the new factor level names are constructed by reordering the factor levels according to the numeric values. If new.order is a chraccter vector, new.order gives the list
of new factor level names. In either case levels omitted from new.order will become missing (NA) values.
If sort is provided (as it is by default): The new factor level names are generated by calling the function specified by sort to the existing factor level names. With sort=mixedsort (the default) the factor levels are sorted so that combined numeric and character strings are sorted in according
to character rules on the character sections (including ignoring case), and the numeric rules for the
numeric sections. See mixedsort for details.

#### Value

A new factor with reordered levels
Author(s)
Gregory R. Warnes <greg@warnes.net>
See Also
factor and reorder

#### Examples
```{r}

# Create a 4 level example factor
trt <- factor( sample( c("PLACEBO", "300 MG", "600 MG", "1200 MG"),
100, replace=TRUE ) )
summary(trt)
# Note that the levels are not in a meaningful order.
# Change the order to something useful..
# - default "mixedsort" ordering
trt2 <- reorder(trt)
summary(trt2)
# - using indexes:
trt3 <- reorder(trt, new.order=c(4, 2, 3, 1))
summary(trt3)
# - using label names:
trt4 <- reorder(trt, new.order=c("PLACEBO", "300 MG", "600 MG", "1200 MG"))
summary(trt4)
# - using frequency
trt5 <- reorder(trt, X=rnorm(100), FUN=mean)resample
49
summary(trt5)
# Drop out the '300 MG' level
trt6 <- reorder(trt, new.order=c("PLACEBO", "600 MG", "1200 MG"))
summary(trt6)
```
