
---
title: "``gdata::resample``"
output: html_document
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(gdata)
```
## ``resample``
Consistent Random Samples and Permutations

#### Description

resample takes a sample of the specified size from the elements of x using either with or without
replacement.

#### Usage
<pre><code>

resample(x, size, replace = FALSE, prob = NULL)

</code></pre>
#### Arguments

* ``x``: A numeric, complex, character or logical vector from which to choose.
* ``size``: Non-negative integer  giving the number of items to choose.
* ``replace ``: Should sampling be with replacement?
* ``prob``: A vector of probability weights for obtaining the elements of the vector being sampled.

#### Details

resample differs from the S/R sample function in resample always considers x to be a vector of
elements to select from, while sample treats a vector of length one as a special case and samples
from 1:x. Otherwise, the functions have identical behavior.

#### Value

Vector of the same length as the input, with the elements permuted.
Author(s)
Gregory R. Warnes <greg@warnes.net>
See Also
sample50
sheetCount

#### Examples
```{r}

## sample behavior differs if first argument is scalar vs vector
sample( c(10) )
sample( c(10,10) )
## resample has the consistent behavior for both cases
resample( c(10) )
resample( c(10,10) )

```

   
