
---
title: "``gdata::sheetCount``"
output: html_document
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(gdata)
```


#### Description

Count or list sheet names in Excel spreadsheet files.

#### Usage

<pre><code>
sheetCount(xls, verbose = FALSE, perl = "perl")
sheetNames(xls, verbose = FALSE, perl = "perl")
</code></pre>

#### Arguments

* ``xls``: File path to spreadsheet. Supports "http://", "https://", and "ftp://" URLS.
* ``verbose``: If TRUE, show additional messages during processing.
* ``perl``: Path to perl interpreter.



#### Examples
```{r}

xlsfile <- system.file("xls", "iris.xls", package = "gdata")
xlsfile
sheetCount(xlsfile)
exampleFile <- file.path(path.package('gdata'),'xls', 'ExampleExcelFile.xls')

exampleFile2007 <- file.path(path.package('gdata'),'xls', 'ExampleExcelFile.xlsx')
sheetCount(exampleFile)

if( 'XLSX' %in% xlsFormats() )
sheetNames(exampleFile2007)

# if XLSX is supported..
````
       
#### Value

sheetCount returns the number of sheets in the spreadsheet. sheetNames returns the names of
sheets in the spreadsheet.
See Also
read.xls, xls2csv.
