
---
title: "``gdata::drop.levels``"
output: html_document
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(gdata)
```
## ``startsWith``
                   
Determine if a character string "starts with" with the specified characters.

#### Description

Determine if a character string "starts with" with the specified characters.

#### Usage
<pre><code>

startsWith(str, pattern, trim=FALSE, ignore.case=FALSE)

</code></pre>
#### Arguments

* ``str``: character vector to test
* pattern characters to check for
* trim Logical flag indicating whether leading whitespace should be removed from str
* before testing for a match.
* ignore.case Logical flag indicating whether case should be ignored when testing for a match.

#### Details

This function returns TRUE for each element of the vector str where pattern occurs at the begin-
ning of the string. If trim is TRUE, leading whitespace is removed from the elements of str before
the test is performed. If ignore.case is TRUE, character case is ignored.

#### Value

Boolean vector of the same length as str.
Author(s)
Gregory R. Warnes <greg@warnes.net>
See Also
substr, trim52
trim

#### Examples
```{r}

## simplest example:
startsWith( 'Testing', 'Test')
## vector examples
s <- c('Testing', ' Testing', 'testing', 'Texting')
names(s) <- s
startsWith(s, 'Test')
# ' Testing', 'testing', and 'Texting' do not match
startsWith(s, 'Test', trim=TRUE)
# Now ' Testing' matches
startsWith(s, 'Test', ignore.case=TRUE) # Now 'testing' matches
```
