
---
title: "``gdata::trimSum``"
output: html_document
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(gdata)
```

Trim a vector such that the last/first value represents the sum of trimmed values

#### Description

trimSum trims (shortens) a vector in such a way that the last or first value represents the sum of
trimmed values. User needs to specify the desired length of a trimmed vector.

#### Usage
<pre><code>

trimSum(x, n, right=TRUE, na.rm=FALSE, ...)

</code></pre>
#### Arguments

* ``x``: numeric, a vector of numeric values
* ``n``: numeric, desired length of the output
* ``right``:  logical, trim on the right/bottom or the left/top side
* ``na.rm``:  logical, remove NA values when applying a function
* ``...``: arguments passed to other methods - currently not used

#### Value

Trimmed vector with a last/first value representing the sum of trimmed values54
unknownToNA
Author(s)
Gregor Gorjanc
See Also
trim

#### Examples
```{r}

x <- 1:10
trimSum(x, n=5)
trimSum(x, n=5, right=FALSE)
x[9] <- NA
trimSum(x, n=5)
trimSum(x, n=5, na.rm=TRUE)
```
