
---
title: "``gdata::update.list``"
output: html_document
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(gdata)
```
## ``update.list``
Update the elements of a list

#### Description

Function to update the elements of a list to contain all of the named elements of a new list, over-
writing elements with the same name, and (optionally) copying unnamed elements.

#### Usage
<pre><code>

## S3 method for class 'list'
update(object,
new,
unnamed=FALSE,
...)58
update.list

</code></pre>
#### Arguments

object
new
unnamed
...
Object to be updated.
List or dataframe containing new elements.
Logical. If TRUE, unnamed elements of new will be appended to object.
optional method arguments (ignored)

#### Value

A new list constructed from the elements of object by merging the elements of old and new with
named items of new replacing the corresponding elements of old. Unnamed elements of new will
be appened unless unnamed=FALSE.
Note
This method can be called directly, or as via the S3 base method for update.
Author(s)
Gregory R. Warnes <greg@warnes.net>
See Also
update, merge

#### Examples
```{r}

old <- list(a=1,b="red",c=1.37)
new <- list(b="green",c=2.4)
update(old, new)
update.list(old,new)
# equivalent
older <- list(a=0, b="orange", 4, 5, 6)
newer <- list(b="purple", 7, 8, 9)
update(older, newer)
# ignores unnamed elements of newer
update(older, newer, unnamed=TRUE) # appends unnamed elements of newer
```

