
---
title: "``gdata::upperTriangle``"
output: html_document
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(gdata)
```


#### Description

Extract or replace the upper/lower triangular portion of a matrix

#### Usage
<pre><code>

upperTriangle(x,
upperTriangle(x,
lowerTriangle(x,
lowerTriangle(x,
diag=FALSE,
diag=FALSE,
diag=FALSE,
diag=FALSE,
byrow=FALSE)
byrow=FALSE) <- value
byrow=FALSE)
byrow=FALSE) <- value

</code></pre>
#### Arguments

* ``x``: Matrix
* ``diag``:  Logical. If TRUE, include the matrix diagonal.
* ``byrow``:  Logical If FALSE, return/replace elements in column-wise order. If TRUE, return/replace elements in row-wise order.
* ``value``: Either a single value or a vector of length equal to that of the current upper/lower triangular. Should be of a mode which can be coerced to that of x.

#### Examples

```{r}

x <- matrix( 1:25, nrow=5, ncol=5)
x
upperTriangle(x)
upperTriangle(x, diag=TRUE)
upperTriangle(x, diag=TRUE, byrow=TRUE)
lowerTriangle(x)
lowerTriangle(x, diag=TRUE)
lowerTriangle(x, diag=TRUE, byrow=TRUE)
upperTriangle(x) <- NA
x
upperTriangle(x, diag=TRUE) <- 1:15
x
lowerTriangle(x) <- NA
x
lowerTriangle(x, diag=TRUE) <- 1:15
x
## Copy lower triangle into upper triangle to make
## the matrix (diagonally) symmetric
x <- matrix(LETTERS[1:25], nrow=5, ncol=5, byrow=TRUE)
x
lowerTriangle(x) = upperTriangle(x, byrow=TRUE)
x
```

#### Value

upperTriangle(x) and lowerTriangle(x) return the upper or lower triangle of matrix x, respectively. The assignment forms replace the upper or lower triangular area of the matrix with the
provided value(s).

Note
By default, the elements are returned/replaced in R’s default column-wise order. Thus lowerTriangle(x) <- upperTriangle(x)
will not yield a symmetric matrix. Instead use:
lowerTriangle(x) <- upperTriangle(x, byrow=TRUE)
or equivalently:
lowerTriangle(x, byrow=TRUE) <- upperTriangle(x)

#### Author(s)
Gregory R. Warnes <greg@warnes.net>60
wideByFactor
See Also
diag, lower.tri, upper.tri
