---
title: "``gdata::wideByFactor``"
output: html_document
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(gdata)
```
Create multivariate data by a given factor

#### Description

``wideByFactor`` modifies data.frame in such a way that variables are “separated” into several columns by factor levels.

#### Usage

<pre><code>
wideByFactor(x, factor, common, sort=TRUE, keepFactor=TRUE)
</code></pre>

#### Arguments

* ``x``: data.frame
* ``factor``:  character, column name of a factor by which variables will be divided
* ``common``: character, column names of (common) columns that should not be divided sort logical, sort resulting data frame by factor levels
* ``keepFactor``: logical, keep the ‘factor’ column



#### Examples
```{r}

n <- 10
f <- 2
tmp <- data.frame(y1=rnorm(n=n),
y2=rnorm(n=n),
f1=factor(rep(letters[1:f], n/2)),
f2=factor(c(rep(c("M"), n/2), rep(c("F"), n/2))),
c1=1:n,
c2=2*(1:n))
wideByFactor(x=tmp, factor="f1", common=c("c1", "c2", "f2"))
wideByFactor(x=tmp, factor="f1", common=c("c1", "c2"))62
```

#### Details

Given data frame is modified in such a way, that output represents a data frame with c + f + n ∗ v columns, where c is a number of common columns for all levels of a factor, f is a factor column, n is a number of levels in factor f and v is a number of variables that should be divided for each level of a factor. Number of rows stays the same!

#### Value

A data frame where divided variables have sort of “diagonalized” structure

#### Author(s)
Gregor Gorjanc

#### See Also
reshape in the stats package, melt and cast in the reshape package
