---
title: "``gdata::write.fwf``"
output: html_document
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(gdata)
```


Write object in fixed width format

#### Description

write.fwf write* ``s``: object in *f*ixed *w*idth *f*ormat.

#### Usage
<pre><code>

write.fwf(x, file="", append=FALSE, quote=FALSE, sep=" ", na="",
rownames=FALSE, colnames=TRUE, rowCol=NULL, justify="left",
formatInfo=FALSE, quoteInfo=TRUE, width=NULL, eol="\n",
qmethod=c("escape", "double"), scientific=TRUE, ...)

</code></pre>
#### Arguments

* ``x``: data.frame or matrix, the object to be written
file character, name of file or connection, look in write.table for more
append logical, append to existing data in file
quote logical, quote data in output
na character, the string to use for missing values i.e. NA in the output
sep character, separator between columns in output
* ``rownames``: logical, print row names
* ``colnames``: logical, print column names
rowCol character, rownames column name
justify character, alignment of character columns; see format
formatInfo logical, return information on number of levels, widths and format
quoteInfo logical, should formatInfo account for quotes
* ``width``:  numeric, width of the columns in the output
eol the character(s) to print at the end of each line (row). For example, ’eol="\r\n"’
will produce Windows’ line endings on a Unix-alike OS, and ’eol="\r"’ will
produce files as expected by Mac OS Excel 2004.
qmethod a character string specifying how to deal with embedded double quote characters
when quoting strings. Must be one of ’"escape"’ (default), in which case the
quote character is escaped in C style by a backslash, or ’"double"’, in which case it is doubled. You can specify just the initial letter.
scientific logical, if TRUE, allow numeric values to be formatted using scientific notation.
... further arguments to format.info and formatwrite.fwf

#### Details

While *F*ixed *w*idth *f*ormat is no longer widely used, it remains common in some disciplines.
Output is similar to print(x) or format(x). Formatting is done completely by format on a column basis. Columns in the output are by default separated with a space i.e. empty column with a width
of one character, but that can be changed with sep argument as passed to write.table via . . . .
As mentioned formatting is done completely by format. 
Arguments can be passed to format via
... to further modify the output. However, note that the returned formatInfo might not properly account for this, since format.info (which is used to collect information about formatting) lacks
the arguments of format.
quote can be used to quote fields in the output. Since all columns of x are converted to character (via format) during the output, all columns will be quoted! If quotes are used, read.table can
be easily used to read the data back into R. Check examples. Do read the details about quoteInfo argument.
Use only *true* character, i.e., avoid use of tabs, i.e., "\t", or similar separators via argument sep.
Width of the separator is taken as the number of characters evaluated via nchar(sep).
Use argument na to convert missing/unknown values. Only single value can be specified. Use NAToUnknown prior to export if you need greater flexibility.
If rowCol is not NULL and rownames=TRUE, rownames will also have column name with rowCol value. This is mainly for flexibility with tools outside R. Note that (at least in R 2.4.0) it is not
"easy" to import data back to R with read.fwf if you also export rownames. This is the reason, that default is rownames=FALSE.
Information about format of output will be returned if formatInfo=TRUE. Returned value is described in value section. This information is gathered by format.info and care was taken to handle
numeric properly. If output contains rownames, values account for this. Additionally, if rowCol is not NULL returned values contain also information about format of rownames.
If quote=TRUE, the output is of course wider due to quotes. Return value (with formatInfo=TRUE) can account for this in two ways; controlled with argument quoteInfo. However, note that there is
no way to properly read the data back to R if quote=TRUE & quoteInfo=FALSE arguments were used for export. quoteInfo applies only when quote=TRUE. Assume that there is a file with quoted
data as shown bellow (column numbers in first three lines are only for demonstration of the values in the output).
123456789 12345678 # for position
123 1234567 123456 # for width with quoteInfo=TRUE
1
12345
1234 # for width with quoteInfo=FALSE
"a" "hsgdh" "
9"
" " "
bb" " 123"
With quoteInfo=TRUE write.fwf will return
colname position width
V1
1
3
V2
5
7
V3
13
6
or (with quoteInfo=FALSE)64
write.fwf
colname position width
V1
2
1
V2
6
5
V3
14
4
Argument width can be used to increase the width of the columns in the output. This argument
is passed to the width argument of format function. 
Values in width are recycled if there is less
values than the number of columns. If the specified width is to short in comparison to the "width"
of the data in particular column, error is issued.

#### Value

Besides its effect to write/export data write.fwf can provide information on format and width. A
data.frame is returned with the following columns:
colname name of the column
nlevels number of unique values (unused levels of factors are dropped), 0 for numeric
column
position starting column number in the output
width width of the column
digits number of digits after the decimal point
exp width of exponent in exponential representation; 0 means there is no exponential
representation, while 1 represents exponent of length one i.e. 1e+6 and 2 1e+06
or 1e+16
Author(s)
Gregor Gorjanc
See Also
format.info, format, NAToUnknown, write.table, read.fwf, read.table and trim

#### Examples
```{r}

## Some data
num <- round(c(733070.345678, 1214213.78765456, 553823.798765678,
1085022.8876545678, 571063.88765456, 606718.3876545678,
1053686.6, 971024.187656, 631193.398765456, 879431.1),
digits=3)
testData <- data.frame(num1=c(1:10, NA),
num2=c(NA, seq(from=1, to=5.5, by=0.5)),
num3=c(NA, num),
int1=c(as.integer(1:4), NA, as.integer(4:9)),
fac1=factor(c(NA, letters[1:9], "hjh")),
fac2=factor(c(letters[6:15], NA)),
cha1=c(letters[17:26], NA),write.fwf
cha2=c(NA, "longer", letters[25:17]),
stringsAsFactors=FALSE)
levels(testData$fac1) <- c(levels(testData$fac1), "unusedLevel")
testData$Date <- as.Date("1900-1-1")
testData$Date[2] <- NA
testData$POSIXt <- as.POSIXct(strptime("1900-1-1 01:01:01",
format="%Y-%m-%d %H:%M:%S"))
testData$POSIXt[5] <- NA
## Default
write.fwf(x=testData)
## NA should be -
write.fwf(x=testData, na="-")
## NA should be -NA-
write.fwf(x=testData, na="-NA-")
## Some other separator than space
write.fwf(x=testData[, 1:4], sep="-mySep-")
## Force wider columns
write.fwf(x=testData[, 1:5], width=20)
## Show effect of 'scienfic' option
testData$num3 <- testData$num3 * 1e8
write.fwf(testData, scientific=TRUE)
write.fwf(testData, scientific=FALSE)
testData$num3 <- testData$num3 / 1e8
## Write to file and report format and fixed width information
file <- tempfile()
formatInfo <- write.fwf(x=testData, file=file, formatInfo=TRUE)
formatInfo
## Read exported data back to R (note +1 due to separator)
## ... without header
read.fwf(file=file, widths=formatInfo$width + 1, header=FALSE, skip=1,
strip.white=TRUE)
## ... with header - via postimport modfication
tmp <- read.fwf(file=file, widths=formatInfo$width + 1, skip=1,
strip.white=TRUE)
colnames(tmp) <- read.table(file=file, nrow=1, as.is=TRUE)
tmp
## ... with header - persuading read.fwf to accept header properly
## (thanks to Marc Schwartz)
read.fwf(file=file, widths=formatInfo$width + 1, strip.white=TRUE,
skip=1, col.names=read.table(file=file, nrow=1, as.is=TRUE))
## ... with header - with the use of quotes
write.fwf(x=testData, file=file, quote=TRUE)
read.table(file=file, header=TRUE, strip.white=TRUE)
6566
xlsFormats
## Tidy up
unlink(file)
```

